---
title: "1. Data set up"
output: 
  html_document:
    df_print: kable
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 2
    number_sections: true
    theme: lumen
---

```{r setup, include=FALSE, cache=FALSE}
options(scipen = NULL, digits = 4) #set to two decimal 
```

<br> 

# Required packages

```{r packages, collapse=T}
library(tidyverse)
library(srvyr)
library(flextable)
library(haven)
library(labelled)
library(huxtable)
```

<br> 

# Folder

```{r}

ddir <- '/Users/joecrowley/R/Tables/Tables function'

```

# Function to display data frames

```{r table quick view}

df_to_dense_flextable <- function(
    df, 
    font_size = 8, 
    padding = 2, 
    merge = NULL, 
    slice = NULL
    ) {
  
  if(!is.null(slice)){df <- df %>% slice(slice)}
  
  ht <- df %>% as_hux %>% 
    # set_number_format(value =  list(function(x) formatC(x, digits = 1, format = "f"))) %>% 
    map_background_color(by_rows("#f5f7fa", "#ffffff")) %>% 
    huxtable::set_background_color(1, everywhere, "grey95") %>% 
    set_wrap(TRUE)
  
  if(!is.null(merge)){ht <- ht %>% merge_repeated_rows() %>% set_valign(value = "middle")}
  
  ft <- huxtable::as_flextable(ht) |>
    flextable::fontsize(size = font_size, part = "all") |>
    flextable::padding(padding = padding, part = "all") |>
    flextable::theme_booktabs() |>
    flextable::autofit()
  
  if(!is.null(merge)){ft <- ft %>% border(
    border = officer::fp_border(color = "grey"),
    # border.top = officer::fp_border(color = "grey"),
    # border.bottom = officer::fp_border(color = "grey"), 
    part = "body"
    )}
  
  format_numeric_cells <- function(ft, data) {
    flextable::set_formatter(
      ft,
      .formatter = function(x) {
        if (is.numeric(x)) {
          formatC(x, format = "f", digits = 1)
        } else {
          as.character(x)
        }
      }
    )
  }
  
  ft <- format_numeric_cells(ft, df)
  
  return(ft)
}

mtcars %>% head() %>% df_to_dense_flextable()
mtcars %>% df_to_dense_flextable(slice = 1:7)
mtcars %>% arrange(cyl) %>% df_to_dense_flextable(slice = 1:7, merge = T)



writeLines(
  c("df_to_dense_flextable <- ", # Assignment needs to be added manually
  deparse(df_to_dense_flextable)), # Extract function code
  paste0(ddir,"/df_to_dense_flextable.R")) # File name is just the function name 

```

# Function to save functions

```{r function to save functions}

write_function <- function(func_name, folder) {
  
  # Get the name of the function as a string
  func_name_str <- deparse(substitute(func_name))
  
  # Build the assignment line
  assign_statement <- paste0(func_name_str, " <- ")
  
  # Build the file path
  file_name <- file.path(folder, paste0(func_name_str, ".R"))
  
  # Get the function object itself
  function_to_export <- get(func_name_str)
  
  # Write to file
  writeLines(
    c(assign_statement, deparse(function_to_export)),
    con = file_name
  )
}

write_function(df_to_dense_flextable, folder = ddir)
write_function(write_function, folder = ddir) # Save out itself for later use

```

<br> 

## Test using saved functions

```{r}

rm(df_to_dense_flextable)
source(paste0(ddir, "/df_to_dense_flextable.R"))

mtcars %>% head() %>% df_to_dense_flextable()

```

<br> 

# Set up data BSA data

```{r data set up}

# Load BSA teaching data
df <- read_sav('/Users/joecrowley/R/Data/BSA Teaching Data/spss/spss25/bsa2019_poverty_open.sav', user_na = T)
names(df)

```

<br>

Display subset of variables to be used in table testing. 

```{r}

df %>% 
  select(welfare2, leftrigh, libauth, RSex, RAgeCat, MuchPov) %>% 
  labelled::look_for()

```

<br>

## Data management {.tabset}

### Clean and select subset of data

Factorise categorical data and removes labelled values from ones I will treat as numeric. 

```{r}

df2 <- df %>% mutate(
  RAgeCat = to_factor(RAgeCat), 
  RSex = to_factor(RSex), 
  skipmeal = to_factor(skipmeal),
  MuchPov = to_factor(MuchPov),
  leftrigh = remove_labels(leftrigh, keep_var_label = T, user_na_to_na = T), 
  welfare2 = remove_labels(welfare2, keep_var_label = T, user_na_to_na = T),
  libauth = remove_labels(libauth, keep_var_label = T, user_na_to_na = T),
  WtFactor = remove_labels(WtFactor, keep_var_label = T, user_na_to_na = T)) %>% 
  select(RAgeCat, RSex, skipmeal, leftrigh, welfare2, libauth, MuchPov, WtFactor)

```

<br> 

### skipmeal

```{r}

df2 %>% count(skipmeal)
df2 <- df2 %>% mutate(skipmeal2 = fct_collapse(skipmeal,
  `Rarely or sometimes` = c("Less than once a month","Once a month","Several times a month"), 
  Often = c("Once a week","Several times a week","Every day"), 
  `DK/REF` = c("Can't choose","Not answered")
))
df2 %>% count(skipmeal2)
```

<br> 

### MuchPov

```{r}

df2 %>% count(MuchPov)
df2 <- df2 %>% mutate(MuchPov2 = fct_collapse(MuchPov,
  `DK/REF` = c("Don`t know","Refusal")
))
df2 %>% count(MuchPov2)
```

<br> 

### libauth

```{r}

df2 %>% count(libauth)
df2 <- df2 %>% 
  mutate(libauth2 = case_when(
    libauth < 2.5 ~ 1, libauth >= 2.5 & libauth <= 3.5 ~ 2, libauth > 3.5 ~ 3, TRUE ~ NA
    ), 
    libauth2 = factor(libauth2, labels = c("Up to 2.5", "2.5 to 3.5", "More than 3.5"))
    )
df2 %>% count(libauth2, libauth)
df2 %>% count(libauth2)
var_label(df2$libauth2) <- "Libertarian-authoritarian scale"
```

<br> 

### leftrigh

```{r}


df2 %>% count(leftrigh)
df2 <- df2 %>% 
  mutate(leftrigh2 = case_when(
    leftrigh < 2.5 ~ 1, leftrigh >= 2.5 & leftrigh <= 3.5 ~ 2, leftrigh > 3.5 ~ 3, TRUE ~ NA
    ), 
    leftrigh2 = factor(leftrigh2, labels = c("Up to 2.5", "2.5 to 3.5", "More than 3.5"))
    )
df2 %>% count(leftrigh2, leftrigh)
df2 %>% count(leftrigh2)
var_label(df2$leftrigh2) <- "Left-right scale"
```

<br> 

### welfare2

```{r}


df2 %>% count(welfare2)
df2 <- df2 %>% 
  mutate(welfare3 = case_when(
    welfare2 < 2.5 ~ 1, welfare2 >= 2.5 & welfare2 <= 3.5 ~ 2, welfare2 > 3.5 ~ 3, TRUE ~ NA
    ), 
    welfare3 = factor(welfare3, labels = c("Up to 2.5", "2.5 to 3.5", "More than 3.5"))
    )
df2 %>% count(welfare3, welfare2)
df2 %>% count(welfare3)
var_label(df2$welfare3) <- "Left-right scale"
```

<br> 

### WtFactor

```{r}

# WtFactor contains weights
df_svy <- df2 %>% as_survey_design(weight = WtFactor)
class(df_svy)

```

<br>

## Save out BSA data

```{r}

save(df_svy, df2, file = paste0(ddir, "/Clean BSA data.Rds"))

```

<br><br>

# Create multicode test data

```{r}

set.seed(123)
n <- 100  # total respondents

# ----- Five multi-coded Yes/No factor variables -----
survey_data <- data.frame(
  Q1_OptionA = factor(sample(c("Yes", "No"), n, replace = TRUE), levels = c("Yes", "No")),
  Q1_OptionB = factor(sample(c("Yes", "No"), n, replace = TRUE), levels = c("Yes", "No")),
  Q1_OptionC = factor(sample(c("Yes", "No"), n, replace = TRUE), levels = c("Yes", "No")),
  Q1_OptionD = factor(sample(c("Yes", "No"), n, replace = TRUE), levels = c("Yes", "No")),
  Q1_OptionE = factor(sample(c("Yes", "No"), n, replace = TRUE), levels = c("Yes", "No"))
)

# Add new multi-coded variables Q2_ChoiceA–E
survey_data$Q2_ChoiceA <- factor(sample(c("Yes", "No"), n, replace = TRUE), levels = c("Yes", "No"))
survey_data$Q2_ChoiceB <- factor(sample(c("Yes", "No"), n, replace = TRUE), levels = c("Yes", "No"))
survey_data$Q2_ChoiceC <- factor(sample(c("Yes", "No"), n, replace = TRUE), levels = c("Yes", "No"))
survey_data$Q2_ChoiceD <- factor(sample(c("Yes", "No"), n, replace = TRUE), levels = c("Yes", "No"))
survey_data$Q2_ChoiceE <- factor(sample(c("Yes", "No"), n, replace = TRUE), levels = c("Yes", "No"))


# ----- Add two non-multi-coded variables -----
# Age group (everyone answered)
survey_data$AgeGroup <- factor(
  sample(c("18–24", "25–34", "35–44", "45+"), n, replace = TRUE),
  levels = c("18–24", "25–34", "35–44", "45+")
)

# Satisfaction (missing values for some respondents → smaller base size)
survey_data$Satisfaction <- factor(
  sample(c("Very satisfied", "Satisfied", "Neutral", "Dissatisfied", "Very dissatisfied", NA), 
         n, replace = TRUE, prob = c(0.15, 0.25, 0.20, 0.15, 0.15, 0.10)),
  levels = c("Very satisfied", "Satisfied", "Neutral", "Dissatisfied", "Very dissatisfied")
)


# Satisfaction (missing values for some respondents → smaller base size)
survey_data$Sex <- factor(
  sample(c("Male", "Female", NA), 
         n, replace = TRUE, prob = c(0.49, 0.49, 0.02)),
  levels = c("Male", "Female")
)

# ----- Add variable labels -----
var_label(survey_data) <- list(
  Q1_OptionA = "Q1: Selected Option A",
  Q1_OptionB = "Q1: Selected Option B",
  Q1_OptionC = "Q1: Selected Option C",
  Q1_OptionD = "Q1: Selected Option D",
  Q1_OptionE = "Q1: Selected Option E",
  Q2_ChoiceA = "Q2: Chose Option A",
  Q2_ChoiceB = "Q2: Chose Option B",
  Q2_ChoiceC = "Q2: Chose Option C",
  Q2_ChoiceD = "Q2: Chose Option D",
  Q2_ChoiceE = "Q2: Chose Option E",
  AgeGroup = "Respondent age group",
  Satisfaction = "Overall satisfaction with service", 
  Sex = "Gender"
)

# ----- Check -----
str(survey_data)
var_label(survey_data)
summary(survey_data$Satisfaction)  # See smaller valid base size

save(survey_data, file = paste0(ddir, "/Multicode data.Rds"))

```
