---
title: "Calculate statistics"
format: html
editor: visual
---

<br>

## Set up

```{r packages, collapse=T, message=F, warning=F}
library(tidyverse)
library(srvyr)
library(flextable)
library(haven)
library(labelled)
library(huxtable)
```

<br>

### Load data, set up functions

```{r}

## Load data
source("Set file paths.R")

## Load functions
source("Scripts/source_folder_r.R")
source_folder_r("Scripts", verbose = T)

data_table_presets <- function(data){
      DT::datatable(
    data,
    class = "compact stripe hover nowrp",
    options = list(
      scrollX = TRUE,
      pageLength = 25,
      autoWidth = TRUE
    ),
    rownames = FALSE
  ) 
}

```

<br>

### Base descriptions

::: panel-tabset
#### Base descriptions BSA

Created for use when testing later.

```{r}

var_descriptions <- rep("Self-completion questionnaire, asked of a random sub-set of respondents", 6)
names(var_descriptions) <- c("leftrigh", "welfare2", "libauth", "libauth2", "leftrigh2", "welfare3") 
var_descriptions

example_of_base_information <- base_information(
  data = df2,
  general_base = "Asked of all respondents", 
  specific_bases = var_descriptions
)

example_of_base_information[[1]]

example_of_base_information[[2]]

example_of_base_information[[3]]

example_of_base_information[[4]]

```

#### Multicodes base information

```{r}

var_descriptions <- rep("Self-completion questionnaire", 5)
names(var_descriptions) <- c("Q1_OptionA", "Q1_OptionB", "Q1_OptionC", "Q1_OptionD", "Q1_OptionE") 


example_of_base_information2 <- base_information(
  data = survey_data,
  general_base = "Asked of all respondents", 
  specific_bases = var_descriptions
)

example_of_base_information2

example_of_base_information2[[1]]

example_of_base_information2[[2]]

example_of_base_information2[[3]]

example_of_base_information2[[4]]

```

<br>
:::

<br>

## Error testing

::: panel-tabset
### Handle nested predictors

Examples of outcome structures. `nested_predictors` won't work, will cause an error. `predictors_one_level` is one that will work, a single level list, each element a character vector of variable length.

```{r}

nested_predictors <- 
list(
  list("MuchPov", "RSex", "RAgeCat"), 
  list(c("skipmeal", "RAgeCat"), "MuchPov2")
) 

nested_predictors

predictors_one_level <- list(c("skipmeal", "RAgeCat"), "MuchPov2")

predictors_one_level

```

<br>

### Confirm list depth

This function then returns list depth. If depth equals 1 then use same predictors for all outcomes. If depth equals 2 then try and use different sets of predictors for different outcomes.

```{r}

list_depth <- function(x) {
  if (!is.list(x)) {
    return(0)  # Not a list → depth 0
  } else if (length(x) == 0) {
    return(1)  # Empty list → depth 1
  } else {
    return(1 + max(sapply(x, list_depth)))
  }
}

write_function(list_depth, folder = "Scripts")

# Use for test to ensure list depth = 1. 
list_depth(nested_predictors)
list_depth(predictors_one_level)

```

<br>

### Confirm variables exist

```{r}

# Returns TRUE if all variables in list appear in data
# Otherwise returns FALSE
vars_exist <- function(variable_list, data){
  
  if(any(grepl("survey", class(data)))){
    df_to_check <- data[["variables"]]
    } else {
      df_to_check <- data
      }
  
  predictors <- variable_list %>% unlist %>% unique
  variables_in_df <- names(df_to_check)
  
  variables_in_both <- intersect(predictors, variables_in_df)
  
  length(predictors) == length(variables_in_both)

  }

vars_exist(data = df2, variable_list = nested_predictors)
vars_exist(data = df_svy, variable_list = nested_predictors)
vars_exist(data = df2, variable_list = list("Random text")) # Random text not a variable name. 
write_function(vars_exist, folder = "Scripts")

```

<br>

### Confirm predictors are factors.

```{r}

check_all_factors <- function(data, variable_list){

  if(any(grepl("survey", class(data)))){
    df_to_check <- data[["variables"]]
    } else {
      df_to_check <- data
      }
  
  df_to_check %>% select(all_of(unlist(variable_list))) %>%
    map_chr(., ~paste0(class(.x), collapse = ", ")) %>% 
    unique == "factor"
}

check_all_factors(data = df2, variable_list = nested_predictors)
check_all_factors(data = df_svy, variable_list = nested_predictors)
write_function(check_all_factors, folder = "Scripts")

```

<br>

### Confirm outcomes not in predictors list

Returns TRUE when no overlap between predictors and outcomes

```{r}

(vector_of_outcomes = c("libauth","welfare2", "leftrigh"))
predictors_one_level

outcomes_not_in_predictors <- function(outcomes, predictors){

  predictor_vector <- unlist(predictors) %>% unique
  overlap_of_predictors_and_outcomes <- intersect(outcomes, predictor_vector)
  length(overlap_of_predictors_and_outcomes) == 0
  
}

outcomes_not_in_predictors(vector_of_outcomes, predictors_one_level)
write_function(outcomes_not_in_predictors, folder = "Scripts")

```

<br>
:::

## Wrapper to combine things - calc_stats

**Checks:**

-   Confirm outcomes not in list of predictors `outcomes_not_in_predictors`.

```{r}

calc_stats <- function(
    data,
    outcomes, # Character vector of outcome variables
    predictors = NULL, # a list, usually each element contains a character vector of predictor variables
    statistics = c("count","mean"),  # default, unweighted count or mean
    conf = NULL, # "se" or "ci"
    base = NULL, 
    pval = NULL, # Whether to compute p-values (if not NULL)
    multicode = TRUE
    ){
  
  # Correct common, non-harmful, and inevitable mistakes #######################
  
  # If `predictors` is a character vector put it in a list
  if(class(predictors) == "character"){predictors <- list(predictors)}
  
  
  # Error handling #############################################################

  # Check variables do, in fact, exist. 
  vector_of_variables_concerned <- c(outcomes, unlist(unique(predictors)))
  test <- vars_exist(data = data, variable_list = vector_of_variables_concerned)
  if (test != TRUE) stop("Some variables you want to use do not exist in the data frame.")

  if(!is.null(predictors)){
    
  # Check outcomes not in predictors
  test <- outcomes_not_in_predictors(outcomes = outcomes, predictors = predictors)
  if (test != TRUE) stop("Outcome appears in predictor list.")

  # Confirm predictors are factors
    test <- check_all_factors(data = data, variable_list = predictors)
    if (test != TRUE) stop("Not all predictors are factor variables. Make them factors.")
  
  # Check predictor list depth is 1
  test <- list_depth(predictors) == 1
  if (test != TRUE) stop("Predictor list should not contained further lists.")
  }
  
  suppressMessages({suppressWarnings({ 
    
  # Where necessary, extract unweighted data from survey objects  
  if(any(str_detect(class(data), "survey"))){
    unweighted_data <- data[["variables"]]
    weighted_data <- data
  } else {
      unweighted_data <- data
      weighted_data <- NULL
  }
    
  # Compute statistics for each outcome/predictor combination 
  individual_tables <- pmap(list(outcomes), function(cur_outcome){
    
    # Extract current outcome variable and filter statistics based on variable type
    single_outcome <- unweighted_data %>% pull(cur_outcome) 
    if(is.factor(single_outcome)){statistic <- str_remove_all(statistics, "mean|median|sum")}
    if(is.numeric(single_outcome)){statistic <- str_remove_all(statistics, "perc|count")}
    
    results <- list() # Store stat results for this combo

    if("mean" %in% statistic){results <- append(results, list(unweighted_mean(unweighted_data, outcomes = cur_outcome, predictors = predictors, conf = conf, base = base)))}
    if("median" %in% statistic){results <- append(results, list(unweighted_median(unweighted_data, outcomes = cur_outcome, predictors = predictors, conf = conf, base = base)))}
    if("sum" %in% statistic){results <- append(results, list(unweighted_sum(unweighted_data, outcomes = cur_outcome, predictors = predictors, conf = conf, base = base)))}
    if("perc" %in% statistic){results <- append(results, list(unweighted_perc(unweighted_data, outcomes = cur_outcome, predictors = predictors, conf = conf, base = base)))}
    if("count" %in% statistic){results <- append(results, list(unweighted_count(unweighted_data, outcomes = cur_outcome, predictors = predictors, conf = conf, base = base)))}
    
    if(!is.null(weighted_data)){
    if("w_mean" %in% statistic){results <- append(results, list(weighted_mean(weighted_data, outcomes = cur_outcome, predictors = predictors, conf = conf, base = base)))}
    if("w_median" %in% statistic){results <- append(results, list(weighted_median(weighted_data, outcomes = cur_outcome, predictors = predictors, conf = conf, base = base)))}
    if("w_sum" %in% statistic){results <- append(results, list(weighted_sum(weighted_data, outcomes = cur_outcome, predictors = predictors, conf = conf, base = base)))}
    if("w_perc" %in% statistic){results <- append(results, list(weighted_perc(weighted_data, outcomes = cur_outcome, predictors = predictors, conf = conf, base = base)))}
    if("w_count" %in% statistic){results <- append(results, list(weighted_count(weighted_data, outcomes = cur_outcome, predictors = predictors, conf = conf, base = base)))}
    }
    
    # Combine results for this outcome
    if(length(results) > 0){results <- results %>% reduce(bind_rows)}

    return(results)
  
  })

  # Merge all results into one table 
  merged_tables <- individual_tables %>% bind_rows
  
  if(!is.null(pval)){
    
    # Extract predictors eligible for p-value testing (only single variables)
    pvalue_preds <- predictors[predictors %>% map_lgl(., ~length(.x) == 1)]
    pvalue_preds <- pvalue_preds %>% unlist %>% unique
    
  pvalues <- list()
  
  # Unweighted p-values
  if(any(statistics %in% c("mean","median","sum","perc","count"))){
    unw_pvalues <- map_return_p_values(data = unweighted_data, outcomes  = outcomes, predictors = pvalue_preds)
    pvalues <- append(pvalues, list(unw_pvalues))
  }

  # Weighted p-values
  if(!is.null(weighted_data)){
    if(any(statistics %in% c("w_mean", "w_median", "w_sum", "w_perc", "w_count"))){
      wgt_pvalues <- map_return_p_values(data = data, outcomes  = outcomes, predictors = pvalue_preds)
      pvalues <- append(pvalues, list(wgt_pvalues))
      }
  }
  
  # Merge p-values into main results
  pvalues <- pvalues %>% bind_rows()
  merged_tables <- merged_tables %>% left_join(pvalues)
  
  } else { 
    # If no p-values requested, still add empty columns
    merged_tables <- merged_tables %>% mutate(p_method = NA, p_value = NA)
  }
  
  # Handle the case of no predictors (total summary) 
  if(is.null(predictors)){merged_tables <- merged_tables %>% mutate(cross_break = "Total")}
  
  # Convert multi-coded values using base info
  # Inserted if statement so that if mulitcodes functions not available, can be excluded. 
  if(multicode == T){
  merged_tables <- convert_multicodes(
    data = merged_tables,  
    base_info = base, 
    keep = "Yes"
    ) 
  }

  return(merged_tables)
  
})})
}

write_function(calc_stats, folder = "Scripts")

```

<br>

#### Tests

::: panel-tabset
##### Test 1

```{r, eval = F}

test1 <- calc_stats(data = df_svy, 
           outcomes = c("RAgeCat","libauth", "welfare3"), 
           predictors = list(c("RSex","skipmeal2","MuchPov2"), "RSex"),
           statistics = c("w_perc","mean"), 
           base = example_of_base_information,
           conf = "ci", pval = T) 


test1 %>% print(n=1000)

test1 %>% pull(p_value)

```

<br>

##### Test 2

```{r, eval = T}
calc_stats(data = df2, 
           outcomes = list("libauth","welfare2", "leftrigh"), 
           predictors = list("RSex", "RAgeCat", "MuchPov2"), 
           pval = T) %>% df_to_dense_flextable()


```

<br>

##### Test 3

```{r, eval = T}
calc_stats(data = df2, 
           outcomes = c("libauth","welfare2", "leftrigh"), 
           predictors = list(c("RSex", "RAgeCat"), "MuchPov2"), 
           pval = T) %>% 
  print(n=1000)

```

<br>

##### Test 4.

```{r, eval = T}

calc_stats(data = df2, 
           outcomes = c("libauth","welfare2", "leftrigh"), 
           predictors = list("RSex", "RAgeCat", "MuchPov2", c("RSex", "MuchPov2")),
           pval = T) %>%
  print(n=1000)


```

<br>

##### Test 5

```{r, eval = T, error = T}

nested_predictors

calc_stats(data = df2, 
           outcomes = c("libauth","welfare2"), 
           predictors = nested_predictors,
           pval = T) %>% df_to_dense_flextable()

```

<br>

##### Test 6

```{r, eval = T}

trial2 <- calc_stats(
    survey_data, 
    base = example_of_base_information2, 
    outcomes = c("Q1_OptionA", "Q1_OptionB", "Q1_OptionC", "Q1_OptionD", "Q1_OptionE", 
                 "Q2_ChoiceA", "Q2_ChoiceB", "Q2_ChoiceC", "Q2_ChoiceD", "Q2_ChoiceE", 
                 "Satisfaction"),
    predictors = "AgeGroup",
    conf = "se") 

trial2

```

##### Test 7

```{r, eval = T}

test7 <- calc_stats(data = df_svy, 
           outcomes = c("RAgeCat","libauth", "welfare3"), 
           ## predictors = list(c("RSex","skipmeal2","MuchPov2")),
           statistics = c("w_perc","mean"), 
           base = example_of_base_information,
           conf = "ci") %>% print(n=1000)

```

##### Test 8

```{r, error = T}

test7 <- calc_stats(data = df_svy, 
           outcomes = c("RAgeCat","libauth", "welfare3", "RSex"), 
           predictors = list("RSex"),
           statistics = c("w_perc","mean"), 
           base = example_of_base_information,
           conf = "ci") %>% print(n=1000)

```

<br>

##### Test 9

```{r, error = T}

test8 <- calc_stats(data = df_svy, 
           outcomes = c("RAgeCat","libauth", "welfare3", "rsex"), 
           # predictors = list("RSex"),
           statistics = c("w_perc","mean"), 
           base = example_of_base_information,
           conf = "ci") %>% print(n=1000)


```
:::
