---
title: "3. Calculate statistics"
format: html
editor: visual
---

## Set up

```{r setup, include=FALSE, cache=FALSE}
options(scipen = NULL, digits = 4) #set to two decimal 
```

<br>

### Required packages

```{r packages, collapse=T}
library(tidyverse)
library(srvyr)
library(flextable)
library(haven)
library(labelled)
library(huxtable)
```

<br>

### Load data, set up functions

```{r}

## Load data
source("Set file paths.R")

## Load functions
source("Scripts/source_folder_r.R")
source_folder_r("Scripts", verbose = T)

```

<br>

### Base descriptions

```{r}

var_descriptions <- rep("Self-completion questionnaire, asked of a random sub-set of respondents", 6)
names(var_descriptions) <- c("leftrigh", "welfare2", "libauth", "libauth2", "leftrigh2", "welfare3") 
var_descriptions

example_of_base_information <- base_information(
  data = df2,
  general_base = "Asked of all respondents", 
  specific_bases = var_descriptions
)

```

<br><br><br>

## Statistics functions overview:

Mean, median and sum for numeric outcomes, percentage and count for categorical ones.

**Weighted functions**:\
\* `weighted_mean`,\
\* `weighted_median`,\
\* `weighted_sum`,\
\* `weighted_perc`,\
\* `weighted_count`.

**Unweighted functions**:\
\* `unweighted_mean`,\
\* `unweighted_median`,\
\* `unweighted_sum`,\
\* `unweighted_perc`,\
\* `unweighted_count`.

An unweighted count is always calculated, stored in unweighted_n. When using `unweighted_count` it is also stored in `estimate` (it is duplicated).

**Arguments**:

-   `data` - a dataframe for unweighted functions, a srvyr object for weighted functions. Unweighted functions will also accept srvyr objects.\
-   `outcomes` - vector of otucome variable names.\
-   `predictors` - list of predictor variable names. Each element is a vector and can be of length \> 1 to produce nested tables.\
-   `conf` - either "se" for standard errors or "ci" for confidence intervals.\
-   `base` - the output of the `base_information` function.

**Data output structure:-** a data frame, column names are...

-   `cross_break` - outcome and predictor variable names separated by ' X '\
-   `outcome` - outcome variable name\
-   `o_lab` - outcome variable label\
-   `o_cat` - outcome variable levels, or duplicate of value in `stat` for numeric statistics.\
-   `predictor`, `p_lab` and `p_cat` - same interpretation as for outcomes, with addition of numbers to differentiate mutliple predictors, `predictor1` for the first predictor and so on.\
-   `stat` - contains the statistic definition.\
-   `estimate`, contains the statistics.\
-   `estimate_se`, `estimate_stat_low` or `estimate_stat_upp` for standard error, lower and upper confidence intervals.\
-   `estimate_ci` present when confidence intervals calculated, but not really used at any point.
-   `base` - unweighted base size for statistics.\
-   `base_description` - the output of `create_bases` for that row's selection of predictor and outcome variables.\
-   `unweighted_n` - cell count.

`cross_break` sometimes missing when only an outcome specified, causes some issues later.

The values of `stat` can be:

-   "mean"\
-   "median"\
-   "sum"\
-   "perc"
-   "count"\
-   "w_mean"\
-   "w_median"\
-   "w_sum"\
-   "w_perc"\
-   "w_count"

<br><br><br>

## Weighted functions {.tabset}

-   Numeric variables - `weighted_mean`.\
-   Numeric variables - `weighted_median`.\
-   Numeric variables - `weighted_sum`.\
-   Categorical variables - `weighted_perc`.\
-   Categorical variables - `weighted_count`.

### Weighted means

```{r weighted mean}

# data <- df_svy
# outcomes <- c("libauth","leftrigh")
# predictors <- list("RSex")
# predictors <- list("RSex","RAgeCat")
# cur_outcome <- "libauth"
# cur_predictor <- "RSex"

weighted_mean <- function(
    data, # a srvyr design object
    outcomes, # a character vector of outcome variables
    predictors = NULL, # a list, each element containing a character vector of predictor variables
    conf = NULL, # "se" or "ci"; returns either standard error or confidence intervals
    base = NULL
) {suppressMessages({suppressWarnings({
  
  output <- map(outcomes, function(cur_outcome) {
    
    base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = cur_outcome)) # edit
    
    # Remove missing data
    one_total_table <- data %>% 
      filter(!is.na(.data[[cur_outcome]])) %>% 
      summarise(estimate = survey_mean(!!sym(cur_outcome), vartype = conf), 
                base = unweighted(n())) %>% 
        mutate("{cur_outcome}" := "w_mean") %>% 
        mutate(outcome = cur_outcome) %>% 
        rename(any_of(c(o_cat = cur_outcome))) %>% 
        mutate(o_lab = attributes(data$variables[[cur_outcome]])$label) %>% 
      # edit
      mutate(base_description = base_defintion) # descriptor label for base 

    # Create cross-breaks
    if(!is.null(predictors)){
    predictor_tables <- map(predictors, function(cur_predictor) { 
      
            # Handle cases with and without predictor variables
        if (length(cur_predictor) > 0) {
          
          # Vector containing predictors and outcomes
          predictor_and_outcome <- c(cur_predictor, cur_outcome)
          base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = predictor_and_outcome)) # edit
          
          one_predictor_table <- data %>%
            # Filter missing values
            filter(rowSums(across(all_of(predictor_and_outcome), ~ is.na(.))) == 0) %>%
            # Group data
            group_by(across(all_of(cur_predictor))) %>% 
            # Weighted mean + base sizes, with grouping vars
            summarise(estimate = survey_mean(!!sym(cur_outcome), vartype = conf), 
                      base = unweighted(n())) %>% 
            # Added for consistency when merged with categorical outcome tables. 
            mutate("{cur_outcome}" := "w_mean") %>% 
            # Standardise names so can stack results across different predictors and outcomes. 
            standardise_names(data = data, preds = cur_predictor, out_var = cur_outcome) %>%
            mutate(cross_break = paste0(cur_predictor, collapse = "_X_")) %>%
            # edit
            mutate(base_description = base_defintion) # descriptor label for base 
        
        }
      
      return(one_predictor_table)
      
    })
    
    predictor_tables <- bind_rows(predictor_tables)
    
    } # Predictors ends
    
    # Bind crossbreaks and frequency table together
    if(!is.null(predictors)){table_for_one_outcome <- bind_rows(one_total_table, predictor_tables)
    } else {table_for_one_outcome <- one_total_table}
    
    table_for_one_outcome <- table_for_one_outcome %>%
      # Record statistic calculated
      mutate(stat = "w_mean") %>%
      # Add 'Total' to predictor category variables for frequency section of the table.
      mutate(across(contains(c("cross_break", "predictor", "p_lab", "p_cat")), ~case_when(is.na(.x) ~ "Total", TRUE ~ .x))) %>%
      # Reorder variables
      select(contains(c("cross_break", "predictor", "p_lab", "p_cat")), outcome, o_lab, o_cat, stat, contains("estimate"), base, base_description) # edit
    
    if(!is.null(conf)){
    if(conf == "ci"){
      table_for_one_outcome <- table_for_one_outcome %>% 
        mutate(estimate_ci = paste0(as.character(estimate_low), " - ", as.character(estimate_upp)))}
    } else { 
      table_for_one_outcome <- table_for_one_outcome %>% mutate(estimate_se = "-", .after = estimate)
      }

    return(table_for_one_outcome)
    
  }) # Outcomes loop ends 
  
  output <- output %>% bind_rows() %>% mutate(unweighted_n = base)
  
  return(output)
  
})})
}

write_function(weighted_mean, folder = ddir)

```

#### Trials {.tabset}

##### Trial 1

```{r}

trial1 <- weighted_mean(df_svy, outcomes = c("libauth","leftrigh"), predictors = list("RSex"))
trial1 %>% glimpse
trial1 %>% df_to_dense_flextable()

```

<br>

##### Trial 2

```{r}

trial2 <- weighted_mean(df_svy, outcomes = c("libauth","leftrigh"), predictors = list("RSex","RAgeCat"), conf = "se") 
trial2 %>% glimpse
trial2 %>% df_to_dense_flextable()

```

<br>

##### Trial 3

```{r}

trial3 <- weighted_mean(df_svy, outcomes = c("libauth","leftrigh"), predictors = list(c("RSex","RAgeCat")), base = example_of_base_information) 
trial3 %>% glimpse
trial3 %>% df_to_dense_flextable()
trial3$base_description %>% unique

```

<br>

##### Trial 4

```{r}

trial4 <- weighted_mean(df_svy, outcomes = c("libauth"), predictors = list(c("RSex","RAgeCat")), conf = "ci") 
trial4 %>% glimpse
trial4 %>% df_to_dense_flextable()

```

<br>

##### Trial 5

```{r}

trial5 <- weighted_mean(df_svy, outcomes = c("libauth","welfare2","leftrigh"), conf = "ci", base = example_of_base_information) 
trial5 %>% glimpse
trial5 %>% df_to_dense_flextable()


```

<br>

### Weighted medians

```{r weighted median}

weighted_median <- function(
    data, # a srvyr design object
    outcomes, # a character vector of outcome variables
    predictors = NULL, # a list, each element containing a character vector of predictor variables
    conf = NULL, # "se" or "ci"; returns either standard error or confidence intervals 
    base = NULL
) {suppressMessages({suppressWarnings({
  
  output <- map(outcomes, function(cur_outcome) {
    # Remove missing data
    base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = cur_outcome)) # edit

    one_total_table <- data %>% 
      filter(!is.na(.data[[cur_outcome]])) %>% 
      summarise(estimate = survey_median(!!sym(zap_labels(cur_outcome)), vartype = conf), 
                base = unweighted(n())) %>% 
        mutate("{cur_outcome}" := "w_median") %>% 
        mutate(outcome = cur_outcome) %>% 
        rename(any_of(c(o_cat = cur_outcome))) %>% 
        mutate(o_lab = attributes(data$variables[[cur_outcome]])$label) %>% 
      mutate(base_description = base_defintion) # descriptor label for base 
  
    # Create cross-breaks
    if(!is.null(predictors)){
    predictor_tables <- map(predictors, function(cur_predictor) { 
      
            # Handle cases with and without predictor variables
        if (length(cur_predictor) > 0) {
          
          # Vector containing predictors and outcomes
          predictor_and_outcome <- c(cur_predictor, cur_outcome)
          base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = predictor_and_outcome))
          
          one_predictor_table <- data %>%
            # Filter missing values
            filter(rowSums(across(all_of(predictor_and_outcome), ~ is.na(.))) == 0) %>%
            # Group data
            group_by(across(all_of(cur_predictor))) %>% 
            # Weighted median + base sizes, with grouping vars
            summarise(estimate = survey_median(!!sym(zap_labels(cur_outcome)), vartype = conf),
                      base = unweighted(n())) %>% 
            # Added for consistency when merged with categorical outcome tables. 
            mutate("{cur_outcome}" := "w_median") %>% 
            # Standardise names so can stack results across different predictors and outcomes. 
            standardise_names(data = data, preds = cur_predictor, out_var = cur_outcome) %>%
            mutate(cross_break = paste0(cur_predictor, collapse = "_X_")) %>%
            mutate(base_description = base_defintion) # descriptor label for base 
        }
      
      return(one_predictor_table)
      
    })
    
    predictor_tables <- bind_rows(predictor_tables)
    
    } # Predictors ends
    
    # Bind crossbreaks and frequency table together
    if(!is.null(predictors)){table_for_one_outcome <- bind_rows(one_total_table, predictor_tables)
    } else {table_for_one_outcome <- one_total_table}
    
    table_for_one_outcome <- table_for_one_outcome %>%
      # Record statistic calculated
      mutate(stat = "w_median") %>%
      # Add 'Total' to predictor category variables for frequency section of the table.
      mutate(across(contains(c("cross_break", "predictor", "p_lab", "p_cat")), ~case_when(is.na(.x) ~ "Total", TRUE ~ .x))) %>%
      # Reorder variables
      select(contains(c("cross_break", "predictor", "p_lab", "p_cat")), outcome, o_lab, o_cat, stat, contains("estimate"), base, base_description) 
    
    if(!is.null(conf)){
      if(conf == "ci"){
        table_for_one_outcome <- table_for_one_outcome %>% 
          mutate(estimate_ci = paste0(as.character(estimate_low), " - ", as.character(estimate_upp)))}
    } else { 
      table_for_one_outcome <- table_for_one_outcome %>% mutate(estimate_se = "-", .after = estimate)
    }

    return(table_for_one_outcome)
    
  }) # Outcomes loop ends 
  
  output <- output %>% bind_rows() %>% mutate(unweighted_n = base)
  
  return(output)
  
})})
}

write_function(weighted_median, folder = ddir)

```

<br>

#### Trials {.tabset}

##### Trial 1

```{r}

trial1 <- weighted_median(df_svy, outcomes = c("libauth","leftrigh"), predictors = list("RSex","RAgeCat")) 
trial1 %>% df_to_dense_flextable()

```

<br>

##### Trial 2

```{r}

trial2 <- weighted_median(df_svy, outcomes = c("libauth"), predictors = list(c("RSex","RAgeCat","skipmeal"))) 
trial2 %>% df_to_dense_flextable()

```

<br>

##### Trial 3

```{r}

trial3 <- weighted_median(df_svy, outcomes = c("libauth"), conf = "ci", base = example_of_base_information) 
trial3 %>% df_to_dense_flextable()

```

<br>

### Weighted sums

```{r weighted sum}

weighted_sum <- function(
    data, # a srvyr design object
    outcomes, # a character vector of outcome variables
    predictors = NULL, # a list, each element containing a character vector of predictor variables
    conf = NULL, # "se" or "ci"; returns either standard error or confidence intervals 
    base = NULL
) {suppressMessages({suppressWarnings({
  
  output <- map(outcomes, function(cur_outcome) {
    
    base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = cur_outcome)) 
    
    # Remove missing data
    one_total_table <- data %>% 
      filter(!is.na(.data[[cur_outcome]])) %>% 
      summarise(estimate = survey_total(!!sym(zap_labels(cur_outcome)), vartype = conf), 
                base = unweighted(n())) %>% 
        mutate("{cur_outcome}" := "w_sum") %>%
        mutate(outcome = cur_outcome) %>% 
        rename(any_of(c(o_cat = cur_outcome))) %>% 
        mutate(o_lab = attributes(data$variables[[cur_outcome]])$label) %>% 
      mutate(base_description = base_defintion) # descriptor label for base 
  
    # Create cross-breaks
    if(!is.null(predictors)){
    predictor_tables <- map(predictors, function(cur_predictor) { 
      
            # Handle cases with and without predictor variables
        if (length(cur_predictor) > 0) {
          
          # Vector containing predictors and outcomes
          predictor_and_outcome <- c(cur_predictor, cur_outcome)
          base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = predictor_and_outcome)) 
          
          one_predictor_table <- data %>%
            # Filter missing values
            filter(rowSums(across(all_of(predictor_and_outcome), ~ is.na(.))) == 0) %>%
            # Group data
            group_by(across(all_of(cur_predictor))) %>% 
            # Weighted median + base sizes, with grouping vars
            summarise(estimate = survey_total(!!sym(zap_labels(cur_outcome)), vartype = conf),
                      base = unweighted(n())) %>% 
            # Added for consistency when merged with categorical outcome tables. 
            mutate("{cur_outcome}" := "w_sum") %>%
            # Standardise names so can stack results across different predictors and outcomes. 
            standardise_names(data = data, preds = cur_predictor, out_var = cur_outcome) %>%
            mutate(cross_break = paste0(cur_predictor, collapse = "_X_")) %>%
            mutate(base_description = base_defintion) # descriptor label for base 
        }
      
      return(one_predictor_table)
      
    })
    
    predictor_tables <- bind_rows(predictor_tables)
    
    } # Predictors ends
    
    # Bind crossbreaks and frequency table together
    if(!is.null(predictors)){table_for_one_outcome <- bind_rows(one_total_table, predictor_tables)
    } else {table_for_one_outcome <- one_total_table}
    
    table_for_one_outcome <- table_for_one_outcome %>%
      mutate(stat = "w_sum") %>%
      # Add 'Total' to predictor category variables for frequency section of the table.
      mutate(across(contains(c("cross_break", "predictor", "p_lab", "p_cat")), ~case_when(is.na(.x) ~ "Total", TRUE ~ .x))) %>%
      # Reorder variables
      select(contains(c("cross_break", "predictor", "p_lab", "p_cat")), outcome, o_lab, o_cat, stat, contains("estimate"), base, base_description) 
        
    if(!is.null(conf)){
      if(conf == "ci"){
        table_for_one_outcome <- table_for_one_outcome %>% 
          mutate(estimate_ci = paste0(as.character(estimate_low), " - ", as.character(estimate_upp)))}
    } else { 
      table_for_one_outcome <- table_for_one_outcome %>% mutate(estimate_se = "-", .after = estimate)
    }

    return(table_for_one_outcome)
    
  }) # Outcomes loop ends 
  
  output <- output %>% bind_rows() %>% mutate(unweighted_n = base)
  
  return(output)
  
})})
}

write_function(weighted_sum, folder = ddir)


```

<br>

#### Trials {.tabset}

##### Trial 1

```{r}
trial1 <- weighted_sum(df_svy, outcomes = c("libauth","leftrigh"), predictors = list("RSex","RAgeCat")) 
trial1 %>% df_to_dense_flextable()
```

<br>

##### Trial 2

```{r}
trial2 <- weighted_sum(df_svy, outcomes = c("libauth"), predictors = list(c("RSex","RAgeCat","skipmeal")), base = example_of_base_information)
trial2 %>% glimpse
trial2 %>% df_to_dense_flextable()
```

<br>

##### Trial 3

```{r}

trial3 <- weighted_sum(df_svy, outcomes = c("libauth", "leftrigh"), predictors = list("RSex"), conf = "ci")
trial3 %>% df_to_dense_flextable()

```

<br><br>

### Weighted percentages

```{r weighted percentages}

weighted_perc <- function(
    data, # a srvyr design object
    outcomes, # a character vector of outcome variables
    predictors = NULL, # a list, each element containing a character vector of predictor variables
    conf = NULL, # "se" or "ci"; returns either standard error or confidence intervals 
    base = NULL
) {suppressMessages({suppressWarnings({
  
  output <- map(outcomes, function(cur_outcome) {
    
    base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = cur_outcome)) # edit
    
    # Remove missing data
    one_total_table <- data %>% 
      filter(!is.na(.data[[cur_outcome]])) %>% 
      group_by(across(all_of(cur_outcome))) %>% 
      summarise(estimate = survey_prop(vartype = conf), 
                unweighted_n = unweighted(n())) %>% 
      mutate(base = sum(unweighted_n, na.rm = T)) %>%
      mutate(outcome = cur_outcome) %>% 
      rename(any_of(c(o_cat = cur_outcome))) %>% 
      mutate(o_lab = attributes(data$variables[[cur_outcome]])$label) %>% 
      mutate(base_description = base_defintion) # descriptor label for base 
  
    # Create cross-breaks
    if(!is.null(predictors)){
    predictor_tables <- map(predictors, function(cur_predictor) { 
  
            # Handle cases with and without predictor variables
        if (length(cur_predictor) > 0) {
          
          # Vector containing predictors and outcomes
          predictor_and_outcome <- c(cur_predictor, cur_outcome)
          base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = predictor_and_outcome)) # edit
          
          one_predictor_table <- data %>%
            # Filter missing values
            filter(rowSums(across(all_of(predictor_and_outcome), ~ is.na(.))) == 0) %>%
            # Group data
            group_by(across(all_of(predictor_and_outcome))) %>% 
            # Weighted percentage + base sizes, with grouping vars
            summarise(estimate = survey_prop(vartype = conf), 
                      unweighted_n = unweighted(n())) %>% 
            mutate(base = sum(unweighted_n, na.rm = T)) %>%
            # Standardise names so can stack results across different predictors and outcomes. 
            standardise_names(data = data, preds = cur_predictor, out_var = cur_outcome) %>%
            mutate(cross_break = paste0(cur_predictor, collapse = "_X_")) %>%
            mutate(base_description = base_defintion) # descriptor label for base 
        }
      
      return(one_predictor_table)
      
    })
    
    predictor_tables <- bind_rows(predictor_tables)
    
    } # Predictors ends
    
    # Bind crossbreaks and frequency table together
    if(!is.null(predictors)){table_for_one_outcome <- bind_rows(one_total_table, predictor_tables)
    } else {table_for_one_outcome <- one_total_table}
    
    table_for_one_outcome <- table_for_one_outcome %>%
      mutate(stat = "w_perc") %>%
      # Add 'Total' to predictor category variables for frequency section of the table.
      mutate(across(contains(c("cross_break", "predictor", "p_lab", "p_cat")), ~case_when(is.na(.x) ~ "Total", TRUE ~ .x))) %>%
      # Reorder variables
      select(contains(c("cross_break", "predictor", "p_lab", "p_cat")), outcome, o_lab, o_cat, stat, contains("estimate"), base, base_description, unweighted_n) 
    
    if(!is.null(conf)){
      if(conf == "ci"){
        table_for_one_outcome <- table_for_one_outcome %>% 
          mutate(estimate_ci = paste0(as.character(estimate_low), " - ", as.character(estimate_upp)))}
    } else { 
      table_for_one_outcome <- table_for_one_outcome %>% mutate(estimate_se = "-", .after = estimate)
    }

    return(table_for_one_outcome)
    
  }) # Outcomes loop ends 
  
  output <- output %>% bind_rows() %>% mutate(unweighted_n = base)
  
  return(output)
  
})})
}

write_function(weighted_perc, folder = ddir)


```

<br>

#### Trials {.tabset}

<br>

##### Trial 1

```{r}
trial <- weighted_perc(df_svy, outcomes = c("skipmeal"), predictors = list("RSex","RAgeCat")) 
trial %>% df_to_dense_flextable()

```

<br>

##### Trial 2

```{r}
trial2 <- weighted_perc(df_svy, outcomes = c("MuchPov"), predictors = list(c("RSex","RAgeCat","skipmeal")), base = example_of_base_information) 
trial2 %>% glimpse
trial2 %>% df_to_dense_flextable()
```

<br><br>

### Weighted count

```{r weighted count}

weighted_count <- function(
    data, # a srvyr design object
    outcomes, # a character vector of outcome variables
    predictors = NULL, # a list, each element containing a character vector of predictor variables
    conf = NULL, # "se" or "ci"; returns either standard error or confidence intervals 
    base = NULL
) {suppressMessages({suppressWarnings({
  
  output <- map(outcomes, function(cur_outcome) {
    
    base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = cur_outcome)) # edit

    # Remove missing data
    one_total_table <- data %>% 
      filter(!is.na(.data[[cur_outcome]])) %>% 
      group_by(across(all_of(cur_outcome))) %>% 
      summarise(estimate = survey_total(vartype = conf), 
                unweighted_n = unweighted(n())) %>% 
      mutate(base = sum(unweighted_n, na.rm = T)) %>%
      mutate(outcome = cur_outcome) %>% 
      rename(any_of(c(o_cat = cur_outcome))) %>% 
      mutate(o_lab = attributes(data$variables[[cur_outcome]])$label) %>% 
      mutate(base_description = base_defintion) # descriptor label for base 
  
  
    # Create cross-breaks
    if(!is.null(predictors)){
    predictor_tables <- map(predictors, function(cur_predictor) { 
  
            # Handle cases with and without predictor variables
        if (length(cur_predictor) > 0) {
          
          # Vector containing predictors and outcomes
          predictor_and_outcome <- c(cur_predictor, cur_outcome)
          base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = predictor_and_outcome)) # edit
          
          one_predictor_table <- data %>%
            # Filter missing values
            filter(rowSums(across(all_of(predictor_and_outcome), ~ is.na(.))) == 0) %>%
            # Group data
            group_by(across(all_of(predictor_and_outcome))) %>% 
            # Weighted percentage + base sizes, with grouping vars
            summarise(estimate = survey_total(vartype = conf), 
                unweighted_n = unweighted(n())) %>% 
            mutate(base = sum(unweighted_n, na.rm = T)) %>%
            # Standardise names so can stack results across different predictors and outcomes. 
            standardise_names(data = data, preds = cur_predictor, out_var = cur_outcome) %>%
            mutate(cross_break = paste0(cur_predictor, collapse = "_X_")) %>%
            mutate(base_description = base_defintion) # descriptor label for base 
        }
      
      return(one_predictor_table)
      
    })
    
    predictor_tables <- bind_rows(predictor_tables)
    
    } # Predictors ends
    
    # Bind crossbreaks and frequency table together
    if(!is.null(predictors)){table_for_one_outcome <- bind_rows(one_total_table, predictor_tables)
    } else {table_for_one_outcome <- one_total_table}
    
    table_for_one_outcome <- table_for_one_outcome %>%
      mutate(stat = "w_count") %>%
      # Add 'Total' to predictor category variables for frequency section of the table.
      mutate(across(contains(c("cross_break", "predictor", "p_lab", "p_cat")), ~case_when(is.na(.x) ~ "Total", TRUE ~ .x))) %>%
      # Reorder variables
      select(contains(c("cross_break", "predictor", "p_lab", "p_cat")), outcome, o_lab, o_cat, stat, contains("estimate"), base, base_description, unweighted_n) 

    if(!is.null(conf)){
      if(conf == "ci"){
        table_for_one_outcome <- table_for_one_outcome %>% 
          mutate(estimate_ci = paste0(as.character(estimate_low), " - ", as.character(estimate_upp)))}
    } else { 
      table_for_one_outcome <- table_for_one_outcome %>% mutate(estimate_se = "-", .after = estimate)
    }
    
    return(table_for_one_outcome)
    
  }) # Outcomes loop ends 
  
  output <- output %>% bind_rows()
  
  return(output)
  
})})
}

write_function(weighted_count, folder = ddir)


```

<br>

#### Trials {.tabset}

##### Trial 1

```{r}

trial <- weighted_count(df_svy, outcomes = c("skipmeal"), predictors = list("RSex","RAgeCat")) 
trial %>% df_to_dense_flextable()

```

<br>

##### Trial 2

```{r}

trial <- weighted_count(df_svy, outcomes = c("MuchPov"), predictors = list(c("RSex","RAgeCat","skipmeal")), base = example_of_base_information) 
trial %>% glimpse
trial %>% df_to_dense_flextable()

```

<br>

##### Trial 3

```{r}

trial <- weighted_count(df_svy, outcomes = c("MuchPov"), conf = "ci") 
trial %>% df_to_dense_flextable()

```

<br><br><br>

## Unweighted statistics functions {.tabset}

Functions are:\
\* `unweighted_mean`.\
\* `unweighted_median`\
\* `unweighted_sum`.\
\* `unweighted_perc`.\
\* `unweighted_count`.

Unweighted count - not optional; always calculated.

<br>

### unweighted_mean

```{r unweighted_mean}

unweighted_mean <- function(
    data, # a data frame
    outcomes, # a character vector of outcome variables
    predictors = NULL, # a list, each element containing a character vector of predictor variables
    conf = NULL, # "se" or "ci"; returns either standard error or confidence intervals 
    base = NULL
) {suppressMessages({suppressWarnings({
  
  output <- map(outcomes, function(cur_outcome) {
    
    base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = cur_outcome)) 
        
    # Remove missing data
    one_total_table <- data %>% 
      filter(!is.na(.data[[cur_outcome]])) %>% 
      summarise(estimate = mean(!!sym(cur_outcome), na.rm = T), 
          n = n(), 
          sd = sd(!!sym(cur_outcome), na.rm = T), 
          estimate_se = sd / sqrt(n), 
          estimate_low = estimate - 1.96 * estimate_se,
          estimate_upp = estimate + 1.96 * estimate_se, 
          base = sum(n)) %>% 
          select(-n, -sd) %>% 
        mutate("{cur_outcome}" := "mean") %>% 
        mutate(outcome = cur_outcome) %>% 
        rename(any_of(c(o_cat = cur_outcome))) %>% 
        mutate(o_lab = attributes(data[[cur_outcome]])$label) %>% 
        mutate(base_description = base_defintion) # descriptor label for base 
  
    # Create cross-breaks
    if(!is.null(predictors)){
    predictor_tables <- map(predictors, function(cur_predictor) { 
      
            # Handle cases with and without predictor variables
        if (length(cur_predictor) > 0) {
          
          # Vector containing predictors and outcomes
          predictor_and_outcome <- c(cur_predictor, cur_outcome)
          base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = predictor_and_outcome)) 
          
          one_predictor_table <- data %>%
            # Filter missing values
            filter(rowSums(across(all_of(predictor_and_outcome), ~ is.na(.))) == 0) %>%
            # Group data
            group_by(across(all_of(cur_predictor))) %>% 
            # Weighted mean + base sizes, with grouping vars
            summarise(estimate = mean(!!sym(cur_outcome), na.rm = T), 
                      n = n(), 
                      sd = sd(!!sym(cur_outcome), na.rm = T), 
                      estimate_se = sd / sqrt(n), 
                      estimate_low = estimate - 1.96 * estimate_se,
                      estimate_upp = estimate + 1.96 * estimate_se, 
                      base = sum(n)) %>% 
                      select(-n, -sd) %>% 
            # Added for consistency when merged with categorical outcome tables. 
            mutate("{cur_outcome}" := "mean") %>% 
            # Standardise names so can stack results across different predictors and outcomes. 
            standardise_names(data = data, preds = cur_predictor, out_var = cur_outcome) %>%
            mutate(cross_break = paste0(cur_predictor, collapse = "_X_")) %>%
            mutate(base_description = base_defintion) # descriptor label for base 
        }
      
      return(one_predictor_table)
      
    })
    
    # Stack tables one on another
    predictor_tables <- bind_rows(predictor_tables)
    
    } # Predictors ends
    
    # Bind crossbreaks and frequency table together
    if(!is.null(predictors)){table_for_one_outcome <- bind_rows(one_total_table, predictor_tables)
    } else {table_for_one_outcome <- one_total_table}
    
    table_for_one_outcome <- table_for_one_outcome %>%
      mutate(stat = "mean") %>%
      # Add 'Total' to predictor category variables for frequency section of the table.
      mutate(across(contains(c("cross_break", "predictor", "p_lab", "p_cat")), ~case_when(is.na(.x) ~ "Total", TRUE ~ as.character(.x)))) %>%
      # Reorder variables
      select(contains(c("cross_break", "predictor", "p_lab", "p_cat")), outcome, o_lab, o_cat, stat, contains("estimate"), base, base_description) 
  
    if(!is.null(conf)){
      if(conf == "ci"){
        table_for_one_outcome <- table_for_one_outcome %>% 
          mutate(estimate_ci = paste0(as.character(estimate_low), " - ", as.character(estimate_upp)))}
    } else { 
      table_for_one_outcome <- table_for_one_outcome %>% mutate(estimate_se = "-", .after = estimate) %>% 
        select(-estimate_low, -estimate_upp)
    }
    
    return(table_for_one_outcome)
    
  }) # Outcomes loop ends 
  
  # Stack tables one on another
  output <- output %>% bind_rows() %>% mutate(unweighted_n = base)
  
  # Either drop standard errors or confidence intervals
  if(!is.null(conf)){
  if(conf == "se"){keep <- c("upp", "low")} else {keep <- "_se"}
    output <- output %>% select(!ends_with(keep))
  }
  
  return(output)
  
})})
}

write_function(unweighted_mean, folder = ddir)


```

<br>

#### Trials {.tabset}

Just use data that is either class of `numeric` or `factor`.

##### Trial 1

```{r}

trial <- unweighted_mean(df2, outcomes = c("libauth","leftrigh"), predictors = list("RSex"))
trial %>% df_to_dense_flextable()

```

<br>

##### Trial 2

```{r}

trial2 <- unweighted_mean(df2, outcomes = c("libauth","leftrigh","welfare2"), predictors = NULL, conf = "ci", base = example_of_base_information)
trial2 %>% glimpse
trial2 %>% df_to_dense_flextable()

```

<br>

##### Trial 3

```{r}

trial3 <- unweighted_mean(df2, outcomes = c("libauth"), predictors = list(c("RSex","RAgeCat")), conf = "se")
trial3 %>% glimpse
trial3 %>% df_to_dense_flextable()

```

<br>

### unweighted_median

```{r unweighted_median}

unweighted_median <- function(
    data, # a data frame
    outcomes, # a character vector of outcome variables
    predictors = NULL, # a list, each element containing a character vector of predictor variables
    conf = NULL, # "se" or "ci"; returns either standard error or confidence intervals 
    base = NULL
) {suppressMessages({suppressWarnings({
  
  output <- map(outcomes, function(cur_outcome) {
    
    base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = cur_outcome)) 
        
    # Remove missing data
    one_total_table <- data %>% 
      filter(!is.na(.data[[cur_outcome]])) %>% 
      summarise(estimate = median(!!sym(cur_outcome), na.rm = T),
                base = n())
      
    if(!is.null(conf)){
      if(conf == "se"){
      median_se <- wrappedtools::medianse(data %>% pull(cur_outcome))
      one_total_table <- one_total_table %>% mutate(estimate_se = median_se)
      } else {
      median_ci <- wrappedtools::median_cl_boot(data %>% pull(cur_outcome))
      one_total_table <- one_total_table %>% mutate(
        estimate_low = median_ci$CIlow,
        estimate_upp = median_ci$CIhigh)
      }
    } else {
      one_total_table <- one_total_table %>% mutate(estimate_se = "-")
    }
    
     one_total_table <- one_total_table %>% 
        mutate("{cur_outcome}" := "median") %>% 
        mutate(outcome = cur_outcome) %>% 
        rename(any_of(c(o_cat = cur_outcome))) %>% 
        mutate(o_lab = attributes(data[[cur_outcome]])$label) %>% 
        mutate(base_description = base_defintion) # descriptor label for base 
  
    # Create cross-breaks
    if(!is.null(predictors)){
    predictor_tables <- map(predictors, function(cur_predictor) { 
      
            # Handle cases with and without predictor variables
        if (length(cur_predictor) > 0) {
          
          # Vector containing predictors and outcomes
          predictor_and_outcome <- c(cur_predictor, cur_outcome)
          base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = predictor_and_outcome)) # edit

          one_predictor_table <- data %>%
            # Filter missing values
            filter(rowSums(across(all_of(predictor_and_outcome), ~ is.na(.))) == 0) %>%
            # Group data
            group_by(across(all_of(cur_predictor))) %>% 
            # Weighted mean + base sizes, with grouping vars
            summarise(estimate = median(!!sym(cur_outcome), na.rm = T),
                base = n())
          
      if(!is.null(conf)){
         if(conf == "se"){
           median_se <- grouped_medianse(data = data, predictors = cur_predictor, outcome = cur_outcome)
           one_predictor_table <- one_predictor_table %>% full_join(median_se)
          }
          else {
            median_ci <- grouped_medianci(data = data, predictors = cur_predictor, outcome = cur_outcome)
            one_predictor_table <- one_predictor_table %>% full_join(median_ci)
          }
      } else {
      one_predictor_table <- one_predictor_table %>% mutate(estimate_se = "-")
      }
      
          # Added for consistency when merged with categorical outcome tables. 
          one_predictor_table <- one_predictor_table %>% mutate("{cur_outcome}" := "median") %>% 
            # Standardise names so can stack results across different predictors and outcomes. 
            standardise_names(data = data, preds = cur_predictor, out_var = cur_outcome) %>%
            mutate(cross_break = paste0(cur_predictor, collapse = "_X_"))  %>%
            mutate(base_description = base_defintion) # descriptor label for base 
            
        }
      
      
      return(one_predictor_table)
      
    })
    
    # Stack tables one on another
    predictor_tables <- bind_rows(predictor_tables)
    
    } # Predictors ends
    
    # Bind crossbreaks and frequency table together
    if(!is.null(predictors)){table_for_one_outcome <- bind_rows(one_total_table, predictor_tables)
    } else {table_for_one_outcome <- one_total_table}
    
    table_for_one_outcome <- table_for_one_outcome %>%
      mutate(stat = "median") %>%
      # Add 'Total' to predictor category variables for frequency section of the table.
      mutate(across(contains(c("cross_break", "predictor", "p_lab", "p_cat")), ~case_when(is.na(.x) ~ "Total", TRUE ~ as.character(.x)))) %>%
      # Reorder variables
      select(contains(c("cross_break", "predictor", "p_lab", "p_cat")), outcome, o_lab, o_cat, stat, contains("estimate"), base, base_description) 
    
    if(!is.null(conf)){
    if(conf == "ci"){
      table_for_one_outcome <- table_for_one_outcome %>% 
        mutate(estimate_ci = paste0(as.character(estimate_low), " - ", as.character(estimate_upp)))
    }
    }
    
    return(table_for_one_outcome)
    
  }) # Outcomes loop ends 
  
  # Stack tables one on another
  output <- output %>% bind_rows() %>% mutate(unweighted_n = base)
  
  # Either drop standard errors or confidence intervals
  if(!is.null(conf)){
  if(conf == "se"){keep <- c("upp", "low")} else {keep <- "_se"}
    output <- output %>% select(!ends_with(keep))
  }
  
  return(output)
  
})})
}

write_function(unweighted_median, folder = ddir)


```

<br>

#### Trials {.tabset}

##### Trial 1

```{r}

trial1 <- unweighted_median(df2, outcomes = c("libauth","leftrigh"), predictors = list("RSex"), base = example_of_base_information, conf = "se")
trial1 %>% glimpse
trial1 %>% df_to_dense_flextable()
trial1$base_description

```

<br>

##### Trial 2

```{r}

unweighted_median(df2, outcomes = c("libauth","leftrigh"), conf = "ci")  %>% df_to_dense_flextable()

```

<br>

##### Trial 3

```{r}

trial3 <- unweighted_median(df2, outcomes = c("libauth"), predictors = list(c("RSex","RAgeCat")), conf = "ci", base = example_of_base_information)
trial3 %>% df_to_dense_flextable()
trial3 %>% glimpse
trial3$base_description


```

<br>

##### Trial 4

```{r}

unweighted_median(df2, outcomes = c("libauth"), predictors = list(c("RSex","MuchPov")))  %>% df_to_dense_flextable()

```

<br>

<br>

##### Trial 5

```{r}

unweighted_median(df2, outcomes = c("libauth"), predictors = list(c("skipmeal2","MuchPov2","RSex")), conf = "ci") %>% df_to_dense_flextable()

```

<br>

### unweighted_sum

```{r unweighted_sum}

unweighted_sum <- function(
    data, # a data frame
    outcomes, # a character vector of outcome variables
    predictors = NULL, # a list, each element containing a character vector of predictor variables
    conf = NULL, # "se" or "ci"; returns either standard error or confidence intervals 
    base = NULL
) {suppressMessages({suppressWarnings({
  
  output <- map(outcomes, function(cur_outcome) {
    
    base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = cur_outcome)) 

    # Remove missing data
    one_total_table <- data %>% 
      filter(!is.na(.data[[cur_outcome]])) %>% 
      summarise(estimate = sum(!!sym(cur_outcome), na.rm = T), 
            base = n(), 
            sd = sd(!!sym(cur_outcome), na.rm = T), 
            estimate_se = sd * sqrt(base), 
            estimate_low = estimate - 1.96 * estimate_se,
            estimate_upp = estimate + 1.96 * estimate_se
            ) %>% select(-sd)
    
     one_total_table <- one_total_table %>% 
        mutate("{cur_outcome}" := "sum") %>% 
        mutate(outcome = cur_outcome) %>% 
        rename(any_of(c(o_cat = cur_outcome))) %>% 
        mutate(o_lab = attributes(data[[cur_outcome]])$label) %>% 
        mutate(base_description = base_defintion) # descriptor label for base 
  
    # Create cross-breaks
    if(!is.null(predictors)){
    predictor_tables <- map(predictors, function(cur_predictor) { 
      
            # Handle cases with and without predictor variables
        if (length(cur_predictor) > 0) {
          
          # Vector containing predictors and outcomes
          predictor_and_outcome <- c(cur_predictor, cur_outcome)
          base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = predictor_and_outcome)) 
          
          one_predictor_table <- data %>%
            # Filter missing values
            filter(rowSums(across(all_of(predictor_and_outcome), ~ is.na(.))) == 0) %>%
            # Group data
            group_by(across(all_of(cur_predictor))) %>% 
            # Weighted mean + base sizes, with grouping vars
            summarise(estimate = sum(!!sym(cur_outcome), na.rm = T), 
            base = n(), 
            sd = sd(!!sym(cur_outcome), na.rm = T), 
            estimate_se = sd * sqrt(base), 
            estimate_low = estimate - 1.96 * estimate_se,
            estimate_upp = estimate + 1.96 * estimate_se
            ) %>% select(-sd)
      
          # Added for consistency when merged with categorical outcome tables. 
          one_predictor_table <- one_predictor_table %>% mutate("{cur_outcome}" := "sum") %>% 
            # Standardise names so can stack results across different predictors and outcomes. 
            standardise_names(data = data, preds = cur_predictor, out_var = cur_outcome) %>%
            mutate(cross_break = paste0(cur_predictor, collapse = "_X_")) %>%
            mutate(base_description = base_defintion) # descriptor label for base 
            
        }
      
      return(one_predictor_table)
      
    })
    
    # Stack tables one on another
    predictor_tables <- bind_rows(predictor_tables)
    
    } # Predictors ends
    
    # Bind crossbreaks and frequency table together
    if(!is.null(predictors)){table_for_one_outcome <- bind_rows(one_total_table, predictor_tables)
    } else {table_for_one_outcome <- one_total_table}
    
    table_for_one_outcome <- table_for_one_outcome %>%
      mutate(stat = "sum") %>% 
      # Add 'Total' to predictor category variables for frequency section of the table.
      mutate(across(contains(c("cross_break", "predictor", "p_lab", "p_cat")), ~case_when(is.na(.x) ~ "Total", TRUE ~ as.character(.x)))) %>%
      # Reorder variables
      select(contains(c("cross_break", "predictor", "p_lab", "p_cat")), outcome, o_lab, o_cat, stat, contains("estimate"), base, base_description) 
    
    if(!is.null(conf)){
      if(conf == "ci"){
        table_for_one_outcome <- table_for_one_outcome %>% 
          mutate(estimate_ci = paste0(as.character(estimate_low), " - ", as.character(estimate_upp)))
      }
    } else {
      table_for_one_outcome <- table_for_one_outcome %>% mutate(estimate_se = "-") %>% 
        select(-estimate_upp, -estimate_low)
    }
    
    return(table_for_one_outcome)
    
  }) # Outcomes loop ends 
  
  # Stack tables one on another
  output <- output %>% bind_rows() %>% mutate(unweighted_n = base)
  
  # Either drop standard errors or confidence intervals
  if(!is.null(conf)){
  if(conf == "se"){keep <- c("upp", "low")} else {keep <- "_se"}
    output <- output %>% select(!ends_with(keep))
  }
  
  return(output)
  
})})
}

write_function(unweighted_sum, folder = ddir)


```

<br>

#### Trials {.tabset}

##### Trial 1

```{r}

unweighted_sum(df2, outcomes = c("libauth","leftrigh"), predictors = list("RSex","RAgeCat")) %>% print(n=100) %>% df_to_dense_flextable()

```

<br>

##### Trial 2

```{r}

trial2 <- unweighted_sum(df2, outcomes = c("libauth"), predictors = list("RSex","RAgeCat", c("skipmeal", "RSex")), conf = "ci", base = example_of_base_information) 
trial2 %>% df_to_dense_flextable()
trial2 %>% glimpse
```

<br>

##### Trial 3

```{r}

trial3 <- unweighted_sum(df2, outcomes = c("welfare2"), predictors = list(c("skipmeal", "RSex", "RAgeCat")), conf = "ci") 
trial3 %>% df_to_dense_flextable()
trial3 %>% glimpse
trial3$base_description %>% unique
```

##### Trial 4

```{r}

unweighted_sum(df2, outcomes = c("welfare2"), conf = "ci", base = example_of_base_information) %>% df_to_dense_flextable()

```

<br>

### unweighted_perc

```{r unweighted_perc}

unweighted_perc <- function(
    data, # a data frame
    outcomes, # a character vector of outcome variables
    predictors = NULL, # a list, each element containing a character vector of predictor variables
    conf = NULL, # "se" or "ci"; returns either standard error or confidence intervals 
    base = NULL
) {suppressMessages({suppressWarnings({
  
  output <- map(outcomes, function(cur_outcome) {
    
    base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = cur_outcome))

    # Remove missing data
    one_total_table <- data %>% 
      filter(!is.na(.data[[cur_outcome]])) %>% 
      count(.data[[cur_outcome]], name = "unweighted_n") %>%    
      mutate(estimate = unweighted_n / sum(unweighted_n), 
             estimate_se = sqrt(estimate * (1 - estimate) / sum(unweighted_n)), 
             estimate_low = (estimate - 1.96 * estimate_se),
             estimate_upp = (estimate + 1.96 * estimate_se),
             base = sum(unweighted_n, na.rm = T)
             ) %>% 
        mutate(outcome = cur_outcome) %>% 
        rename(any_of(c(o_cat = cur_outcome))) %>% 
        mutate(o_lab = attributes(data[[cur_outcome]])$label) %>% 
        mutate(base_description = base_defintion) # descriptor label for base 
  
    # Create cross-breaks
    if(!is.null(predictors)){
    predictor_tables <- map(predictors, function(cur_predictor) { 
      
            # Handle cases with and without predictor variables
        if (length(cur_predictor) > 0) {
          
          # Vector containing predictors and outcomes
          predictor_and_outcome <- c(cur_predictor, cur_outcome)
          base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = predictor_and_outcome)) 
          
          one_predictor_table <- data %>%
            # Filter missing values
            filter(rowSums(across(all_of(predictor_and_outcome), ~ is.na(.))) == 0) %>%
            # Group data
            group_by(across(all_of(predictor_and_outcome))) %>% 
            summarise(unweighted_n = n()) %>%
            group_by(across(all_of(cur_predictor))) %>% 
            mutate(estimate = unweighted_n / sum(unweighted_n, na.rm = T), 
               estimate_se = sqrt(estimate * (1 - estimate) / sum(unweighted_n)), 
               estimate_low = (estimate - 1.96 * estimate_se),
               estimate_upp = (estimate + 1.96 * estimate_se),
               base = sum(unweighted_n, na.rm = T)
             )
      
          # Added for consistency when merged with categorical outcome tables. 
          one_predictor_table <- one_predictor_table %>% 
            # Standardise names so can stack results across different predictors and outcomes. 
            standardise_names(data = data, preds = cur_predictor, out_var = cur_outcome) %>%
            mutate(cross_break = paste0(cur_predictor, collapse = "_X_")) %>%
            mutate(base_description = base_defintion) # descriptor label for base 
            
        }
      
      return(one_predictor_table)
      
    })
    
    # Stack tables one on another
    predictor_tables <- bind_rows(predictor_tables)
    
    } # Predictors ends
    
    # Bind crossbreaks and frequency table together
    if(!is.null(predictors)){table_for_one_outcome <- bind_rows(one_total_table, predictor_tables)
    } else {table_for_one_outcome <- one_total_table}
    
    table_for_one_outcome <- table_for_one_outcome %>%
      mutate(stat = "perc") %>%
      # Add 'Total' to predictor category variables for frequency section of the table.
      mutate(across(contains(c("cross_break", "predictor", "p_lab", "p_cat")), ~case_when(is.na(.x) ~ "Total", TRUE ~ as.character(.x)))) %>%
      # Reorder variables
      select(contains(c("cross_break", "predictor", "p_lab", "p_cat")), outcome, o_lab, o_cat, stat, contains("estimate"), unweighted_n, base, base_description) 
    
    if(!is.null(conf)){
      if(conf == "ci"){
        table_for_one_outcome <- table_for_one_outcome %>% 
          mutate(estimate_ci = paste0(as.character(estimate_low), " - ", as.character(estimate_upp)))
      }
    } else {
      table_for_one_outcome <- table_for_one_outcome %>% mutate(estimate_se = "-") %>% 
        select(-estimate_upp, -estimate_low)
    }
    

    return(table_for_one_outcome)
    
  }) # Outcomes loop ends 
  
  # Stack tables one on another
  output <- output %>% bind_rows()
  
  # Either drop standard errors or confidence intervals
  if(!is.null(conf)){
  if(conf == "se"){keep <- c("upp", "low")} else {keep <- "_se"}
    output <- output %>% select(!ends_with(keep))
  }
  
  return(output)
  
})})
}

write_function(unweighted_perc, folder = ddir)


```

<br>

#### Trials {.tabset}

##### Trial 1

```{r}

trial1 <- unweighted_perc(df2, outcomes = c("skipmeal"), 
               predictors = list("RSex"), 
               conf = "ci", 
               base = example_of_base_information)
trial1 %>% df_to_dense_flextable()
trial1 %>% glimpse

```

<br>

##### Trial 2

```{r}

unweighted_perc(df2, outcomes = c("skipmeal","RAgeCat"), 
               predictors = list("RSex","MuchPov"), 
               conf = "ci") %>% df_to_dense_flextable()

```

<br>

##### Trial 3

```{r}

trial3 <- 
  unweighted_perc(df2, outcomes = c("MuchPov"), 
               predictors = list(c("RSex","RAgeCat")), 
               conf = "se") 
trial3 %>% df_to_dense_flextable()
trial3 %>% glimpse

```

##### Trial 4

```{r}

trial4 <- unweighted_perc(df2, outcomes = c("MuchPov","RSex","RAgeCat"), 
               conf = NULL) 

trial4 %>% df_to_dense_flextable()

```

<br>

### unweighted_count

```{r unweighted_count}

unweighted_count <- function(
    data, # a data frame
    outcomes, # a character vector of outcome variables
    predictors = NULL, # a list, each element containing a character vector of predictor variables
    conf = NULL, # "se" or "ci"; returns either standard error or confidence intervals 
    base = NULL
) {suppressMessages({suppressWarnings({
  
  output <- map(outcomes, function(cur_outcome) {
    
    base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = cur_outcome)) # edit

    # Remove missing data
    one_total_table <- data %>% 
      filter(!is.na(.data[[cur_outcome]])) %>% 
      count(.data[[cur_outcome]], name = "estimate") %>%    
      mutate(base = sum(estimate, na.rm = T), 
             prop = estimate / base,
             estimate_se = sqrt(base * prop * (1 - prop)),
             estimate_low = (estimate - 1.96 * estimate_se),
             estimate_upp = (estimate + 1.96 * estimate_se),
             ) %>% 
      select(-prop) %>% 
      mutate(outcome = cur_outcome) %>% 
      rename(any_of(c(o_cat = cur_outcome))) %>% 
      mutate(o_lab = attributes(data[[cur_outcome]])$label) %>% 
      mutate(base_description = base_defintion) # descriptor label for base 
  
    # Create cross-breaks
    if(!is.null(predictors)){
    predictor_tables <- map(predictors, function(cur_predictor) { 
      
            # Handle cases with and without predictor variables
        if (length(cur_predictor) > 0) {
          
          # Vector containing predictors and outcomes
          predictor_and_outcome <- c(cur_predictor, cur_outcome)
          base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = predictor_and_outcome)) 
          
          one_predictor_table <- data %>%
            # Filter missing values
            filter(rowSums(across(all_of(predictor_and_outcome), ~ is.na(.))) == 0) %>%
            # Group data
            group_by(across(all_of(predictor_and_outcome))) %>% 
            summarise(estimate = n()) %>%
            group_by(across(all_of(cur_predictor))) %>% 
            mutate(
              base = sum(estimate, na.rm = T),
              prop = estimate / sum(base), 
              estimate_se = sqrt(base * prop * (1 - prop)),
              estimate_low = (estimate - 1.96 * estimate_se),
              estimate_upp = (estimate + 1.96 * estimate_se)
             ) %>% select(-prop)
      
          # Added for consistency when merged with categorical outcome tables. 
          one_predictor_table <- one_predictor_table %>% 
            # Standardise names so can stack results across different predictors and outcomes. 
            standardise_names(data = data, preds = cur_predictor, out_var = cur_outcome) %>%
            mutate(cross_break = paste0(cur_predictor, collapse = "_X_")) %>%
            mutate(base_description = base_defintion) # descriptor label for base 
            
        }
      
      return(one_predictor_table)
      
    })
    
    # Stack tables one on another
    predictor_tables <- bind_rows(predictor_tables)
    
    } # Predictors ends
    
    # Bind crossbreaks and frequency table together
    if(!is.null(predictors)){table_for_one_outcome <- bind_rows(one_total_table, predictor_tables)
    } else {table_for_one_outcome <- one_total_table}
    
    table_for_one_outcome <- table_for_one_outcome %>%
      mutate(stat = "count", unweighted_n = estimate) %>%
      # Add 'Total' to predictor category variables for frequency section of the table.
      mutate(across(contains(c("cross_break", "predictor", "p_lab", "p_cat")), ~case_when(is.na(.x) ~ "Total", TRUE ~ as.character(.x)))) %>%
      # Reorder variables
      select(contains(c("cross_break", "predictor", "p_lab", "p_cat")), outcome, o_lab, o_cat, stat, contains("estimate"), unweighted_n, base, base_description) 
    
    if(!is.null(conf)){
      if(conf == "ci"){
        table_for_one_outcome <- table_for_one_outcome %>% 
          mutate(estimate_ci = paste0(as.character(estimate_low), " - ", as.character(estimate_upp)))
      }
    } else {
      table_for_one_outcome <- table_for_one_outcome %>% mutate(estimate_se = "-") %>% 
        select(-estimate_upp, -estimate_low)
    }
    
    

    return(table_for_one_outcome)
    
  }) # Outcomes loop ends 
  
  # Stack tables one on another
  output <- output %>% bind_rows()
  
  # Either drop standard errors or confidence intervals
  if(!is.null(conf)){
  if(conf == "se"){keep <- c("upp", "low")} else {keep <- "_se"}
    output <- output %>% select(!ends_with(keep))
  }
  
  return(output)
  
})})
}

write_function(unweighted_count, folder = ddir)


```

<br>

#### Trials {.tabset}

##### Trial 1

```{r}

trial1 <- 
  unweighted_count(
    df2, 
    outcomes = c("skipmeal"), 
    predictors = list("RSex"), 
    conf = "ci", 
    base = example_of_base_information) 
trial1 %>% df_to_dense_flextable()
trial1 %>% glimpse()

```

<br>

##### Trial 2

```{r}

unweighted_count(df2, outcomes = c("skipmeal","RAgeCat"), 
               predictors = list("RSex","MuchPov"), 
               conf = "ci") %>% 
  df_to_dense_flextable()

```

<br>

##### Trial 3

```{r}

unweighted_count(df2, outcomes = c("MuchPov"), 
               predictors = list(c("RSex","RAgeCat")), 
               conf = "se") %>% 
  df_to_dense_flextable()

```

##### Trial 3

```{r}

unweighted_count(df2, outcomes = c("MuchPov","RSex","RAgeCat"), 
               conf = NULL) %>% 
  df_to_dense_flextable()

```

<br><br><br>

## A wrapper for functions calculating statistics

**Arguments**, the same as in the individual functions.

One new argument - `statistics` - the values allowed are:

-   "mean"\
-   "median"\
-   "sum"\
-   "perc"\
-   "count"\
-   "w_mean"\
-   "w_median"\
-   "w_sum"\
-   "w_perc"\
-   "w_count"

Multiple arguments = c("mean", "count")

**Data output structure:-** remains the same as for individual statistic functions.

```{r calc_stats}

# data <- df2
# outcomes <- "MuchPov"
# predictors <- "RSex"
# statistics <- "count"
# conf <- "se"
# base <- NULL
# 
# rm(data)
# rm(outcomes)
# rm(predictors)
# rm(statistics)
# rm(conf)
# rm(base)

calc_stats <- function(
    data,
    outcomes, 
    predictors = NULL,
    statistics = c("count","mean"),  # default, unweighted count or mean
    conf = "se", # or "ci"
    base = NULL, 
    pval = NULL
    ){
  suppressMessages({suppressWarnings({
    
  if(any(str_detect(class(data), "survey"))){
    unweighted_data <- data[["variables"]]
    weighted_data <- data
  } else {
      unweighted_data <- data
      weighted_data <- NULL
      }
  
  # Process each outcome variable
  individual_tables <- map(outcomes, function(cur_outcome) {
    
    single_outcome <- unweighted_data %>% pull(cur_outcome)
    if(is.factor(single_outcome)){statistics <- str_remove_all(statistics, "mean|median|sum")}
    if(is.numeric(single_outcome)){statistics <- str_remove_all(statistics, "perc|count")}
    
    results <- list()
    
    if("mean" %in% statistics){results <- append(results, list(unweighted_mean(unweighted_data, outcomes = cur_outcome, predictors = predictors, conf = conf, base = base)))}
    if("median" %in% statistics){results <- append(results, list(unweighted_median(unweighted_data, outcomes = cur_outcome, predictors = predictors, conf = conf, base = base)))}
    if("sum" %in% statistics){results <- append(results, list(unweighted_sum(unweighted_data, outcomes = cur_outcome, predictors = predictors, conf = conf, base = base)))}
    if("perc" %in% statistics){results <- append(results, list(unweighted_perc(unweighted_data, outcomes = cur_outcome, predictors = predictors, conf = conf, base = base)))}
    if("count" %in% statistics){results <- append(results, list(unweighted_count(unweighted_data, outcomes = cur_outcome, predictors = predictors, conf = conf, base = base)))}
    
    if(!is.null(weighted_data)){
    if("w_mean" %in% statistics){results <- append(results, list(weighted_mean(weighted_data, outcomes = cur_outcome, predictors = predictors, conf = conf, base = base)))}
    if("w_median" %in% statistics){results <- append(results, list(weighted_median(weighted_data, outcomes = cur_outcome, predictors = predictors, conf = conf, base = base)))}
    if("w_sum" %in% statistics){results <- append(results, list(weighted_sum(weighted_data, outcomes = cur_outcome, predictors = predictors, conf = conf, base = base)))}
    if("w_perc" %in% statistics){results <- append(results, list(weighted_perc(weighted_data, outcomes = cur_outcome, predictors = predictors, conf = conf, base = base)))}
    if("w_count" %in% statistics){results <- append(results, list(weighted_count(weighted_data, outcomes = cur_outcome, predictors = predictors, conf = conf, base = base)))}
    }
    
    if(length(results) > 0){results <- results %>% reduce(bind_rows)}
    
    return(results)
    
  })
  
  merged_tables <- individual_tables %>% bind_rows
  
  if(!is.null(pval)){
  pvalues <- list()
  if(any(statistics %in% c("mean","median","sum","perc","count"))){
    unw_pvalues <- map_return_p_values(data = data, outcomes  = outcomes, predictor = predictors)
    pvalues <- append(pvalues, list(unw_pvalues))
  }

  if(!is.null(weighted_data)){
    if(any(statistics %in% c("w_mean", "w_median", "w_sum", "w_perc", "w_count"))){
      wgt_pvalues <- map_return_p_values(data = data, outcomes  = outcomes, predictor = predictors)
      pvalues <- append(pvalues, list(wgt_pvalues))
      }
  }
  
  pvalues <- pvalues %>% bind_rows()
  merged_tables <- merged_tables %>% left_join(pvalues)
  
  } else { 
    merged_tables <- merged_tables %>% mutate(p_method = NA, p_value = NA)
  }
  
  if(is.null(predictors)){merged_tables <- merged_tables %>% mutate(cross_break = "Total")}

  return(merged_tables)
  
})})
}

write_function(calc_stats, folder = "Scripts")


```

<br><br><br>

#### Trials {.tabset}

##### Trial 1

```{r}

names(df2)
test <- calc_stats(data = df2, 
           outcomes = c("RAgeCat","MuchPov"), 
           predictors = list("RSex"), 
           statistics = c("perc","w_perc"), 
           conf = "se")

test %>% glimpse()

test %>% rmarkdown::paged_table()

```

<br>

##### Trial 2

```{r}

calc_stats(data = df2, 
           outcomes = c("RAgeCat","MuchPov"), 
           predictors = list("RSex"), 
           statistics = "perc", 
           conf = "se") %>% 
  rmarkdown::paged_table()


```

<br>

##### Trial 3

```{r}

test <- calc_stats(data = df_svy, 
           outcomes = c("RAgeCat"), 
           predictors = list(c("RSex","skipmeal2","MuchPov2")),
           statistics = c("perc"), 
           conf = "ci", 
           base = example_of_base_information)

test %>% glimpse()

test %>% rmarkdown::paged_table()

```

<br>

##### Trial 4

```{r}

calc_stats(data = df_svy, 
           outcomes = c("RAgeCat","libauth"), 
           predictors = list(c("RSex","skipmeal2","MuchPov2")),
           statistics = c("w_perc","mean"), 
           base = example_of_base_information,
           conf = "ci") %>% 
  rmarkdown::paged_table()

```

<br><br>

## Identify Multicodes {.tabset}

### Steps overview

This code identifies variables with: a) a stem divider, I will use ": ", b) a matching set of values on the left hand side of the stem divider, c) No more than 2 unique values in its levels, and d) the same base size.

So, the variable labels will be split in two around ": ". A multicode set is one where all the left hand sides of the resulting variable are the same.

But how to identify matching sets?

Once done it will replace variable label with the left hand part of the stem.

The response levels will be filtered to 'yes' or equivalent. 'yes' will be a specifiable argument, e.g. could be 'mentioned'.

For simplicity, I'll **assume** binaries be coded consistently, e.g. people don't feed in a combination of yes/no and mentioned/not mentioned questions.

It will replace variable level == 'yes' with the right hand part of the stem.

Variable name will be reduced to the stem that is consistent across all variables in that set. Not dealt yet with the possibility that there is no consistent stem.

Base description will be updated to have a single base description for the variable as a whole, using the left hand part of the stem as the variable label.

This new base description will be silently added to the object with *base description* in it, in these trials that is `example_of_base_information`.

Should I then drop duplicates from the base description info? Probably, yes.

<br>

### Test data

**Base information**

```{r}

var_descriptions <- rep("Self-completion questionnaire", 5)
names(var_descriptions) <- c("Q1_OptionA", "Q1_OptionB", "Q1_OptionC", "Q1_OptionD", "Q1_OptionE") 


example_of_base_information2 <- base_information(
  data = survey_data,
  general_base = "Asked of all respondents", 
  specific_bases = var_descriptions
)

example_of_base_information2

```

<br>

**Test tables**

```{r}

trial1 <- calc_stats(
    survey_data, 
    base = example_of_base_information2, 
    outcomes = c("Q1_OptionA", "Q1_OptionB", "Q1_OptionC", "Q1_OptionD", "Q1_OptionE", 
                 "Q2_ChoiceA", "Q2_ChoiceB", "Q2_ChoiceC", "Q2_ChoiceD", "Q2_ChoiceE",
                 "AgeGroup", "Satisfaction"),
    conf = "se") 

trial1
trial1 %>% glimpse

trial2 <- calc_stats(
    survey_data, 
    base = example_of_base_information2, 
    outcomes = c("Q1_OptionA", "Q1_OptionB", "Q1_OptionC", "Q1_OptionD", "Q1_OptionE", 
                 "Q2_ChoiceA", "Q2_ChoiceB", "Q2_ChoiceC", "Q2_ChoiceD", "Q2_ChoiceE", 
                 "Satisfaction"),
    predictors = "AgeGroup",
    conf = "se") 

trial2
trial2 %>% glimpse
trial2$base_description %>% unique()

trial3 <- calc_stats(
    survey_data, 
    base = example_of_base_information2, 
    outcomes = c("Q1_OptionA", "Q1_OptionB", "Q1_OptionC", "Q1_OptionD", "Q1_OptionE", 
                 "Q2_ChoiceA", "Q2_ChoiceB", "Q2_ChoiceC", "Q2_ChoiceD", "Q2_ChoiceE"),
    predictors = list(c("AgeGroup","Satisfaction")),
    conf = "se") 

trial3
trial3 %>% glimpse
trial3$base_description %>% unique()

```

<br><br>

### Convenience function to reduce variable names to a common stem

This takes a vector of variable names and returns a single character value with the common parts of the strings in that vector, assuming there is one.

```{r}

# Example vector of multi-coded variable names
vars <- c("Q1_OptionA", "Q1_OptionB", "Q1_OptionC", "Q1_OptionD", "Q1_OptionE")

# Find longest common prefix
common_prefix <- function(x) {
  split_names <- strsplit(x, "")
  min_length <- min(lengths(split_names))
  prefix <- character(0)
  for (i in seq_len(min_length)) {
    chars <- sapply(split_names, `[`, i)
    if (length(unique(chars)) == 1) {
      prefix <- c(prefix, chars[1])
    } else {
      break
    }
  }
  paste0(prefix, collapse = "")
}

write_function(common_prefix, folder = ddir)

common_prefix(vars)
# [1] "Q1_Option"

set1 <- c("Q2_Fruit_Apple", "Q2_Fruit_Banana", "Q2_Fruit_Cherry", "Q2_Fruit_Grape", "Q2_Fruit_Mango")
common_prefix(set1)

set6 <- c("Q4FruitApple", "Q4FruitBanana", "Q4FruitCherry", "Q4FruitGrape", "Q4FruitMango")
common_prefix(set6)

# If no common prefix, returns a string of zero length which will cause an error. Hmmmm. 
common_prefix(c("last","frui"))

```

<br>

### Intial variable screening

The first stage narrows the data frame received from `calc_stats` down to suitable rows:

1.  `stat` must equal "perc" or "count",\
2.  `o_lab` must contain ": ",\
3.  The outcome variable must contain either 1 or 2 levels,\
4.  Those levels must include the *relevant* value, for now "yes". Could be user specified.

<br>

5.  For these rows of data it them creates a variable called `left_stem`, which contains the values on the left hand side of ": ". This will be the variable label for the new multicode variable.

<br>

6.  There must be more than one variable with a consistent left_stem value.\
7.  The `base` value must be the same within unique values of left_stem.

The resulting output is a dataframe with only the relevant rows of data from the output of `calc_stats`.

```{r}

multis <- trial2 %>% 
  filter(stat == "perc" | stat == "count") %>% # Multicodes relevant only for categorical data
  filter(grepl(": ", o_lab)) %>% # Label must contain ": "
  group_by(across(contains(c("cross_break", "p_cat"))), outcome) %>% # Group by outcome variable
  mutate(lev_num = max(row_number())) %>% # Count number of levels in each variable
  group_by(outcome) %>% 
  mutate(lev_relevant = case_when(any(o_cat == "Yes") ~ 1, TRUE ~ 0)) %>% # Any of variable's levels equal yes? 
  filter(
    lev_num <= 2 & # Only use variables with 1 or 2 levels
    lev_relevant == 1 # Only use variables with a relevant level, here 'yes'
    )  %>% 
  mutate(
    left_stem = str_split_i(o_lab, ": ", 1) # Create left variable label stem 
    ) %>% 
  group_by(across(contains(c("crossbreak", "p_cat"))), left_stem) %>% # Group by predictors and left stem
  mutate(
    stem_count = n_distinct(outcome), # number of different variables with that variable stem 
    base_count = n_distinct(base) # Number of unique values in base
    ) %>% 
  filter(stem_count > 1) %>% # Only use variables where right stem recurs more than once
  filter(base_count == 1)  # Only use variables where base is unique within left_stem

multis

# Create an identifier vector for multicode rows from: 
#  -  cross_break (all the predictors), 
#  -  and the outcome variable.
# Then reduce that to a vector of unique values
multicode_row_identifiers <-  multis %>% unite(ident, c(cross_break, outcome)) %>% pull(ident) %>% unique
multicode_row_identifiers

# Use `multicode_row_identifiers` to drop these rows from the original table.
single_codes <- trial2 %>% unite(ident, c(cross_break, outcome), remove = F) %>% 
  filter(!ident %in% multicode_row_identifiers) %>% 
  select(-ident)

```

### Reorganise data identified as multicoded

```{r}

# The next step is done separately for each unique multicode set and predictor combination 
# Identified with left_stem2, created below. 
# Results returned as a list from map()

# If the column "cross_break" exists in the dataframe 'multis'...
if("cross_break" %in% names(multis)){
  # ...then create a new column 'left_stem2' by combining 'left_stem' and 'cross_break'
  multis <- multis %>% mutate(left_stem2 = paste0(left_stem, " - ", cross_break))
} else {
  # ...otherwise, just copy 'left_stem' into 'left_stem2'
  multis <- multis %>% mutate(left_stem2 = left_stem)
}

multis


# The following line is commented out — for testing 
# stem <- unique_stems[2]


# Get all unique values of 'left_stem2' in the data
unique_stems <- multis$left_stem2 %>% unique

# Loop over each unique value of 'left_stem2'
result <- map(unique_stems, function(stem) {
  
  # Filter 'multis' to only the rows matching the current stem
  multis2 <- multis %>% 
    filter(left_stem2 == stem) 
  
  # Save the original variable label from the first row (for later use)
  old_variable_label <- multis2$o_lab[1]
  
  # Step 1: Create a 'right_stem' by splitting 'o_lab' on ": " and taking the second part
  # Step 2: Replace 'o_lab' with the value of 'left_stem'
  multis2 <- multis2 %>%
    mutate(
      right_stem = str_split_i(o_lab, ": ", 2), 
      o_lab = left_stem
    ) %>% 
    # Step 3: Keep only rows where 'o_cat' == "Yes"
    filter(o_cat == "Yes") %>% 
    # Step 4: Replace 'o_cat' with 'right_stem' values, and shorten 'outcome' to its common prefix
    mutate(
      o_cat = right_stem, 
      outcome = common_prefix(outcome)
    ) 
  
  # Get the unique new variable name
  new_variable_name <- multis2$outcome %>% unique()
  # Get the unique new variable label
  new_variable_label <- multis2$o_lab %>% unique
  # Name the label vector with the new variable name
  names(new_variable_label) <- new_variable_name
  
  # Get the existing base description from the first row
  existing_base_description <- multis2$base_description[1]
  
  # If the base description contains " X ", split it into two parts
  if(str_detect(existing_base_description, " X ")){
    existing_base_description_2 <- str_split(existing_base_description, " X ") %>% unlist
  } else {
    # Otherwise, keep it as is
    existing_base_description_2 <- existing_base_description
  }
  
  # Create a logical index for which part(s) match the old variable label
  index <- str_detect(existing_base_description_2, old_variable_label)
  reverse_index <- !str_detect(existing_base_description_2, old_variable_label)
  
  # Extract the matching part(s) and remove anything after ":- "
  existing_base_description_3 <- existing_base_description_2[index] %>% str_split_i(., ":- ", 1)
  
  # Create a revised base label by appending the new variable label
  revised_base_label <- paste0(existing_base_description_3, ":- ", new_variable_label)
  names(revised_base_label) <- new_variable_name
  
  # If the base description originally had " X ", reassemble with the unchanged part(s)
  if(str_detect(existing_base_description, " X ")){
    remainder_of_base_description <- existing_base_description_2[reverse_index] 
    revised_base_description <- paste(
      revised_base_label, 
      remainder_of_base_description, 
      sep = " X ")
  } else {
    revised_base_description <- revised_base_label
  }
  
  # Update 'base_description' in the filtered dataset
  multis2 <- multis2 %>% mutate(base_description = revised_base_description)
  
  # Logical test: stop execution if the new variable name already exists in 'example_of_base_information2'
  if (new_variable_name %in% names(example_of_base_information2)) {
    stop("Error: New multicode variable name already in data.")
  } 
  
  # Return a list containing:
  # 1. The updated 'multis2' dataframe
  # 2. The revised base label
  # 3. The new variable label
  return(list(multis2, revised_base_label, new_variable_label))
  
}) 
# End of map() loop

# Combine all first elements of 'result' (the dataframes) into one big dataframe
tables <- bind_rows(map(result, ~(.x[[1]])))

# Extract all base labels from the results, flatten into one vector, and remove duplicates
new_base_descriptors <- map(result, ~(.x[[2]])) %>% unlist
new_base_descriptors <- new_base_descriptors[!duplicated(new_base_descriptors)]

# Extract all variable labels from the results, flatten, and remove duplicates
new_variable_labels <- map(result, ~(.x[[3]])) %>% unlist
new_variable_labels <- new_variable_labels[!duplicated(new_variable_labels)]

# Make a temporary copy of 'example_of_base_information2'
example_of_base_information2_temp <- example_of_base_information2

# Append new base descriptors and labels to positions [[2]], [[3]], and [[4]] of that object
example_of_base_information2_temp[[2]] <- c(example_of_base_information2[[2]], new_base_descriptors)
example_of_base_information2_temp[[3]] <- c(example_of_base_information2[[3]], new_variable_labels)
example_of_base_information2_temp[[4]] <- c(example_of_base_information2[[4]], new_variable_labels)

# Overwrite the original 'example_of_base_information2' object in the global environment with the updated version
example_of_base_information2 <<- example_of_base_information2_temp

multis2 <- tables %>% ungroup() %>% select(-lev_num, -lev_relevant, -left_stem, -stem_count, -base_count, -left_stem2, -right_stem)

# Review: original data, multicode data, and single code data...
trial2 %>% glimpse
multis2 %>% glimpse
multicode_row_identifiers %>% glimpse

# Bind single and multicode data together
bind_rows(single_codes, multis2)

```

<br>

### Fuction

```{r}

  # filter(stat == "perc" | stat == "count") %>% # Multicodes relevant only for categorical data
  # filter(grepl(": ", o_lab)) %>% # Label must contain ": "
  # group_by(across(contains(c("cross_break", "p_cat"))), outcome) %>% # Group by outcome variable
  # mutate(lev_num = max(row_number())) %>% # Count number of levels in each variable
  # group_by(outcome) %>% 
  # mutate(lev_relevant = case_when(any(o_cat == "Yes") ~ 1, TRUE ~ 0)) %>% # Any of variable's levels equal yes? 

# data <- trial3
# base_info <- example_of_base_information2
# rm(data)
# rm(base_info)
# rm(keep)

convert_multicodes <- function(
  data, 
  base_info = NULL, 
  keep = "Yes"){
  
  if(!is.null(base_info)){base_info_name_as_string <- deparse(substitute(base_info))}
  
  multis <- data %>% 
    filter(stat == "perc" | stat == "count" | stat == "w_count" | stat == "w_perc") %>% # Multicodes relevant only for categorical data
    filter(grepl(": ", o_lab)) %>% # Label must contain ": "
    
    # Count number of levels in each variable
    group_by(across(contains(c("cross_break", "p_cat"))), outcome) %>% # Group by outcome variable + crossbreak set + levels
    mutate(lev_num = max(row_number())) %>% 
    
    # Any of variable's levels equal yes?
    group_by(outcome) %>% 
    mutate(lev_relevant = case_when(any(o_cat == "Yes") ~ 1, TRUE ~ 0)) %>%  
    
    # filter non-relevant variables
    filter(
      lev_num <= 2 & # Only use variables with 1 or 2 levels
      lev_relevant == 1 # Only use variables with a relevant level, here 'yes'
      )  %>% 
    mutate(
      left_stem = str_split_i(o_lab, ": ", 1) # Create left variable label stem 
      ) %>% 
    group_by(across(contains(c("crossbreak", "p_cat"))), left_stem) %>% # Group by predictors and left stem
    mutate(
      stem_count = n_distinct(outcome), # number of different variables with that variable stem 
      base_count = n_distinct(base) # Number of unique values in base
      ) %>% 
    filter(stem_count > 1) %>% # Only use variables where right stem recurs more than once
    filter(base_count == 1)  # Only use variables where base is unique within left_stem
  
  if(nrow(multis) > 0){
  
  # Create an identifier vector for multicode rows from: 
  #  -  cross_break (all the predictors), 
  #  -  and the outcome variable.
  # Then reduce that to a vector of unique values
  multicode_row_identifiers <-  multis %>% unite(ident, contains(c("cross_break", "outcome"))) %>% pull(ident) %>% unique
  multicode_row_identifiers
  
  # Use `multicode_row_identifiers` to drop these rows from the original table.
  single_codes <- data %>% unite(ident, contains(c("cross_break", "outcome")), remove = F) %>% 
    filter(!ident %in% multicode_row_identifiers) %>% 
    select(-ident)

  # The next step is done separately for each unique multicode set and predictor combination 
  # Identified with left_stem2, created below. 
  # Results returned as a list from map()
  
  # If the column "cross_break" exists in the dataframe 'multis'...
  if("cross_break" %in% names(multis)){
    # ...then create a new column 'left_stem2' by combining 'left_stem' and 'cross_break'
    multis <- multis %>% mutate(left_stem2 = paste0(left_stem, " - ", cross_break))
  } else {
    # ...otherwise, just copy 'left_stem' into 'left_stem2'
    multis <- multis %>% mutate(left_stem2 = left_stem)
  }
  
  # Get all unique values of 'left_stem2' in the data
  unique_stems <- multis$left_stem2 %>% unique
  # stem <- unique_stems[[2]]
  
    # Loop over each unique value of 'left_stem2'
    result <- map(unique_stems, function(stem) {
    
    # Filter 'multis' to only the rows matching the current stem
    multis2 <- multis %>% filter(left_stem2 == stem) 
    
    # Save the original variable label from the first row (for later use)
    old_variable_label <- multis2$o_lab[1]
    
    # Step 1: Create a 'right_stem' by splitting 'o_lab' on ": " and taking the second part
    # Step 2: Replace 'o_lab' with the value of 'left_stem'
    multis2 <- multis2 %>% ungroup() %>%
      mutate(
        right_stem = str_split_i(o_lab, ": ", 2), 
        o_lab = left_stem
      ) %>% 
      # Step 3: Keep only rows where 'o_cat' == "Yes"
      filter(o_cat == "Yes") %>% 
      # Step 4: Replace 'o_cat' with 'right_stem' values, and shorten 'outcome' to its common prefix
      mutate(
        o_cat = right_stem, 
        outcome = common_prefix(outcome)
      ) 
    
    # Skip base description related steps where base_info NULL
    if(!is.null(base_info)){
        
      # Get the unique new variable name
      new_variable_name <- multis2$outcome %>% unique()
      # Get the unique new variable label
      new_variable_label <- multis2$o_lab %>% unique
      # Name the label vector with the new variable name
      names(new_variable_label) <- new_variable_name
      
      # Get the existing base description from the first row
      existing_base_description <- multis2$base_description[1]
      
      # If the base description contains " X ", split it into two parts
      if(str_detect(existing_base_description, " X ")){
        existing_base_description_2 <- str_split(existing_base_description, " X ") %>% unlist
      } else {
        # Otherwise, keep it as is
        existing_base_description_2 <- existing_base_description
      }
      
      # Create a logical index for which part(s) match the old variable label
      index <- str_detect(existing_base_description_2, old_variable_label)
      reverse_index <- !str_detect(existing_base_description_2, old_variable_label)
      
      # Extract the matching part(s) and remove anything after ":- "
      existing_base_description_3 <- existing_base_description_2[index] %>% str_split_i(., ":- ", 1)
      
      # Create a revised base label by appending the new variable label
      revised_base_label <- paste0(existing_base_description_3, ":- ", new_variable_label)
      names(revised_base_label) <- new_variable_name
      
      # If the base description originally had " X ", reassemble with the unchanged part(s)
      if(str_detect(existing_base_description, " X ")){
        remainder_of_base_description <- existing_base_description_2[reverse_index] 
        revised_base_description <- paste0(
          c(revised_base_label, remainder_of_base_description), 
          collapse = " X ")
      } else {
        revised_base_description <- revised_base_label
      }
      
      # Update 'base_description' in the filtered dataset
      multis2 <- multis2 %>% mutate(base_description = revised_base_description)
      
      # Logical test: drop existing variable names from 'base_info'
      if (new_variable_name %in% names(base_info[[3]])) {
        
        keep_item_2 <- which(!(base_info[[2]] %>% names()) %in% new_variable_name)
        keep_item_3 <- which(!(base_info[[3]] %>% names()) %in% new_variable_name)
        keep_item_4 <- which(!(base_info[[4]] %>% names()) %in% new_variable_name)
        base_info[[2]] <- base_info[[2]][keep_item_2]
        base_info[[3]] <- base_info[[3]][keep_item_3]
        base_info[[4]] <- base_info[[4]][keep_item_4]

        # stop("Error: New multicode variable name already in data.")
      } 
      
      # Where base description provided, return a list containing:
      #  1. The updated 'multis2' dataframe
      #  2. The revised base label
      #  3. The new variable label
      return(list(multis2, revised_base_label, new_variable_label))
    
    } else {
      
      return(list(multis2)) # Otherwise, simply return data frame, in a list so map() below will work
      
    }
    
    }) # End of map() loop
  
  # Combine all first elements of 'result' (the dataframes) into one big dataframe
  tables <- bind_rows(map(result, ~(.x[[1]])))
  
  # Skip base description related steps where base_info NULL
  if(!is.null(base_info)){
    
    # Extract all base labels from the results, flatten into one vector, and remove duplicates
    new_base_descriptors <- map(result, ~(.x[[2]])) %>% unlist
    new_base_descriptors <- new_base_descriptors[!duplicated(new_base_descriptors)]
    
    # Extract all variable labels from the results, flatten, and remove duplicates
    new_variable_labels <- map(result, ~(.x[[3]])) %>% unlist
    new_variable_labels <- new_variable_labels[!duplicated(new_variable_labels)]
    
    # Make a temporary copy of 'base_info'
    example_of_base_info2_temp <- base_info
    
    # If those variable names already exist in base descriptions information, then drop them...
    base_info[[2]] <- base_info[[2]][which(!base_info[[2]] %in% new_base_descriptors)]
    base_info[[3]] <- base_info[[3]][which(!base_info[[3]] %in% new_variable_labels)]
    base_info[[4]] <- base_info[[4]][which(!base_info[[4]] %in% new_variable_labels)]

    # Append new base descriptors and labels to positions [[2]], [[3]], and [[4]] of that object
    example_of_base_info2_temp[[2]] <- c(base_info[[2]], new_base_descriptors)
    example_of_base_info2_temp[[3]] <- c(base_info[[3]], new_variable_labels)
    example_of_base_info2_temp[[4]] <- c(base_info[[4]], new_variable_labels)
    
    # Overwrite the original 'base_info' object in the global environment with the updated version
    assign(base_info_name_as_string, example_of_base_info2_temp, envir = .GlobalEnv)
    # base_info <<- example_of_base_info2_temp
  
  }
  
  # Create multicode object to export
  multis2 <- tables %>% 
    ungroup() %>% # Otherwise, cannot drop left_stem
    # Drop temporary variables
    select(-lev_num, -lev_relevant, -left_stem, -stem_count, -base_count, -left_stem2, -right_stem)
  
  # Bind single and multicode data together
  multicoded_and_single_code_data <- bind_rows(single_codes, multis2)
  
  return(multicoded_and_single_code_data)
  
  } else {return(data)}
  
}

write_function(convert_multicodes, folder = ddir)


```

<br>

#### Test multicode conversion {.tabset}

##### Test 1

```{r}

convert_multicodes(
  data = trial1, 
  base_info = example_of_base_information2, 
  keep = "Yes") %>% df_to_dense_flextable()

```

<br>

##### Test 2

```{r}
convert_multicodes(
  data = trial2, 
  base_info = example_of_base_information2, 
  keep) %>% 
  df_to_dense_flextable()

```

<br>

##### Test 3

```{r}
rm(base_info)
convert_multicodes(
  data = trial3 %>% mutate(base=NA,base_description=NA), 
  base_info = NULL,
  # base_info = example_of_base_information2, 
  keep) %>% 
  df_to_dense_flextable()

convert_multicodes(
  data = trial3, 
  base_info = example_of_base_information2,
  keep) %>% 
  df_to_dense_flextable()

```

<br><br><br>

## calc_stats final

The updated version of calc_stats below now incorporates some additional steps, over and above calc_stats further up in this script:

-   Multicode handling now dealt with within calc_stats itself.\
-   It also allows for different sets of predictors to be used with each outcome, if needed.\
-   I also now remembered to set `conf` to `NULL` by default.

```{r}
## For testing... 
# data <- df2
# outcomes <- "MuchPov"
# predictors <- "RSex"
# statistics <- "count"
# conf <- "se"
# base <- NULL
# 
# rm(data)
# rm(outcomes)
# rm(predictors)
# rm(statistics)
# rm(conf)
# rm(base)

```

<br>

### Handle nested predictors

```{r}

# Predictor variables which should change for each outcome 
# Here, suitable where two outcomes only
# Top level of predictor list needs to be same length as outcomes. 

nested_predictors <- 
list(
  list("MuchPov", "RSex", "RAgeCat"), 
  list(c("skipmeal", "RAgeCat"), "MuchPov2")
) 

predictors_one_level <- list(c("skipmeal", "RAgeCat"), "MuchPov2")
```

This function then returns list depth. If depth equals 1 then use same predictors for all outcomes. If depth equals 2 then try and use different sets of predictors for different outcomes.

```{r}

list_depth <- function(x) {
  if (!is.list(x)) {
    return(0)  # Not a list → depth 0
  } else if (length(x) == 0) {
    return(1)  # Empty list → depth 1
  } else {
    return(1 + max(sapply(x, list_depth)))
  }
}

write_function(list_depth, folder = ddir)

list_depth(nested_predictors)
list_depth(predictors_one_level)
```

This function is there to handle occasions where data has list depth of greater than 2, in these cases predictors are ignored (set to NULL). Also, if predictors are in a vector rather than a list they are put in a list (this is just a cleaning thing, it doesn't affect output).

```{r}
manage_predictors <- function(predictors, outcomes){
  
  if(is.null(predictors)){
    
    pred <- rep(list(predictors), length(outcomes))
    
    } else if (is.list(predictors)){
      
      ldepth <- list_depth(predictors)
      
      if(ldepth > 3){pred <- NULL} else {pred <- predictors}
      
    } else {
      
      pred <- list(predictors)
      
    }
  
  if(!is.null(predictors)){
  if(list_depth(pred) == 1){pred <- pred %>% list}
  
  pred_lenth <- length(pred)
  if(pred_lenth !=1  & pred_lenth != length(outcomes)){pred <- pred[1]}
  pred_lenth <- length(pred)
  if(pred_lenth == 1){pred <- rep(list(pred), length(outcomes)) %>% flatten}
  }
  
  return(pred)
  
}

write_function(manage_predictors, folder = ddir)

nested_predictors
manage_predictors(predictors = nested_predictors, outcomes = "RSex") 
manage_predictors(predictors = nested_predictors, outcomes = c("RSex", "libauth")) 
manage_predictors(predictors = nested_predictors, outcomes = c("RSex", "libauth", "welfare2"))

predictors_one_level
manage_predictors(predictors_one_level, outcomes = "RSex")
manage_predictors(predictors_one_level, outcomes = c("RSex", "libauth")) 

manage_predictors("RSex", outcomes = "RAgeCat")
manage_predictors("RSex", outcomes = c("RAgeCat", "libauth")) 

manage_predictors(NULL, outcomes = c("RAgeCat", "libauth")) 


```

<br>

### Revised function

```{r}

# outcomes <- c("RSex", "RAgeCat", "test")
# nested_predictors <- rev(nested_predictors)

calc_stats <- function(
    data,
    outcomes, # Character vector of outcome variables
    predictors = NULL, # a list, usually each element contains a character vector of predictor variables
    statistics = c("count","mean"),  # default, unweighted count or mean
    conf = NULL, # "se" or "ci"
    base = NULL, 
    pval = NULL # Whether to compute p-values (if not NULL)
    ){
  suppressMessages({suppressWarnings({
    
  # Where necessary, extract unweighted data from survey objects  
  if(any(str_detect(class(data), "survey"))){
    unweighted_data <- data[["variables"]]
    weighted_data <- data
  } else {
      unweighted_data <- data
      weighted_data <- NULL
  }
  
  # Organise predictors (see manage_predictors above)
  managed_preds <- manage_predictors(predictors = predictors, outcomes = outcomes) 
  
  # Compute statistics for each outcome/predictor combination 
  individual_tables <- pmap(list(outcomes, managed_preds), function(cur_outcome, predictor_set){
    
    # Extract current outcome variable and filter statistics based on variable type
    single_outcome <- unweighted_data %>% pull(cur_outcome) 
    if(is.factor(single_outcome)){statistic <- str_remove_all(statistics, "mean|median|sum")}
    if(is.numeric(single_outcome)){statistic <- str_remove_all(statistics, "perc|count")}
    
    results <- list() # Store stat results for this combo

    if("mean" %in% statistic){results <- append(results, list(unweighted_mean(unweighted_data, outcomes = cur_outcome, predictors = predictor_set, conf = conf, base = base)))}
    if("median" %in% statistic){results <- append(results, list(unweighted_median(unweighted_data, outcomes = cur_outcome, predictors = predictor_set, conf = conf, base = base)))}
    if("sum" %in% statistic){results <- append(results, list(unweighted_sum(unweighted_data, outcomes = cur_outcome, predictors = predictor_set, conf = conf, base = base)))}
    if("perc" %in% statistic){results <- append(results, list(unweighted_perc(unweighted_data, outcomes = cur_outcome, predictors = predictor_set, conf = conf, base = base)))}
    if("count" %in% statistic){results <- append(results, list(unweighted_count(unweighted_data, outcomes = cur_outcome, predictors = predictor_set, conf = conf, base = base)))}
    
    if(!is.null(weighted_data)){
    if("w_mean" %in% statistic){results <- append(results, list(weighted_mean(weighted_data, outcomes = cur_outcome, predictors = predictor_set, conf = conf, base = base)))}
    if("w_median" %in% statistic){results <- append(results, list(weighted_median(weighted_data, outcomes = cur_outcome, predictors = predictor_set, conf = conf, base = base)))}
    if("w_sum" %in% statistic){results <- append(results, list(weighted_sum(weighted_data, outcomes = cur_outcome, predictors = predictor_set, conf = conf, base = base)))}
    if("w_perc" %in% statistic){results <- append(results, list(weighted_perc(weighted_data, outcomes = cur_outcome, predictors = predictor_set, conf = conf, base = base)))}
    if("w_count" %in% statistic){results <- append(results, list(weighted_count(weighted_data, outcomes = cur_outcome, predictors = predictor_set, conf = conf, base = base)))}
    }
    
    # Combine results for this outcome/predictor
    if(length(results) > 0){results <- results %>% reduce(bind_rows)}

    return(results)
  
  })

  # Merge all results into one table 
  merged_tables <- individual_tables %>% bind_rows
  
  if(!is.null(pval)){
    
    # Extract predictors eligible for p-value testing (only single variables)
    pvalue_preds <- flatten(managed_preds) 
    pvalue_preds <- pvalue_preds[pvalue_preds %>% map_lgl(., ~length(.x) == 1)]
    pvalue_preds <- pvalue_preds %>% unlist %>% unique
    
  pvalues <- list()
  
  # Unweighted p-values
  if(any(statistics %in% c("mean","median","sum","perc","count"))){
    unw_pvalues <- map_return_p_values(data = unweighted_data, outcomes  = outcomes, predictors = pvalue_preds)
    pvalues <- append(pvalues, list(unw_pvalues))
  }

  # Weighted p-values
  if(!is.null(weighted_data)){
    if(any(statistics %in% c("w_mean", "w_median", "w_sum", "w_perc", "w_count"))){
      wgt_pvalues <- map_return_p_values(data = data, outcomes  = outcomes, predictors = pvalue_preds)
      pvalues <- append(pvalues, list(wgt_pvalues))
      }
  }
  
  # Merge p-values into main results
  pvalues <- pvalues %>% bind_rows()
  merged_tables <- merged_tables %>% left_join(pvalues)
  
  } else { 
    # If no p-values requested, still add empty columns
    merged_tables <- merged_tables %>% mutate(p_method = NA, p_value = NA)
  }
  
  # Handle the case of no predictors (total summary) 
  if(is.null(predictors)){merged_tables <- merged_tables %>% mutate(cross_break = "Total")}
  
  # Convert multi-coded values using base info
  merged_tables <- convert_multicodes(
    data = merged_tables,  
    base_info = base, 
    keep = "Yes"
    ) 

  return(merged_tables)
  
})})
}

write_function(calc_stats, folder = ddir)

```

<br>

#### Tests {.tabset}

##### Test 1

```{r}

test1 <- calc_stats(data = df_svy, 
           outcomes = c("RAgeCat","libauth", "welfare3"), 
           predictors = list(c("RSex","skipmeal2","MuchPov2"), "RSex"),
           statistics = c("w_perc","mean"), 
           base = example_of_base_information,
           conf = "ci", pval = T) 


test1 %>% print(n=1000)

test1 %>% pull(p_value)

```

<br>

##### Test 2

```{r}
calc_stats(data = df2, 
           outcomes = list("libauth","welfare2", "leftrigh"), 
           predictors = list("RSex", "RAgeCat", "MuchPov2"), 
           pval = T) %>% df_to_dense_flextable()


```

<br>

##### Test 3

```{r}
calc_stats(data = df2, 
           outcomes = c("libauth","welfare2", "leftrigh"), 
           predictors = list("RSex", "RAgeCat", "MuchPov2"), 
           pval = T) %>% 
  print(n=1000)

```

<br>

##### Test 4.

```{r}

calc_stats(data = df2, 
           outcomes = c("libauth","welfare2", "leftrigh"), 
           predictors = list("RSex", "RAgeCat", "MuchPov2", c("RSex", "MuchPov2")),
           pval = T) %>%
  print(n=1000)


```

<br>

##### Test 5

```{r}

calc_stats(data = df2, 
           outcomes = c("libauth","welfare2"), 
           predictors = nested_predictors,
           pval = T) %>% df_to_dense_flextable()

```

<br>

##### Test 6

```{r}

trial2 <- calc_stats(
    survey_data, 
    base = example_of_base_information2, 
    outcomes = c("Q1_OptionA", "Q1_OptionB", "Q1_OptionC", "Q1_OptionD", "Q1_OptionE", 
                 "Q2_ChoiceA", "Q2_ChoiceB", "Q2_ChoiceC", "Q2_ChoiceD", "Q2_ChoiceE", 
                 "Satisfaction"),
    predictors = "AgeGroup",
    conf = "se") 

trial2

```

##### Test 7

```{r}

test7 <- calc_stats(data = df_svy, 
           outcomes = c("RAgeCat","libauth", "welfare3"), 
           ## predictors = list(c("RSex","skipmeal2","MuchPov2")),
           statistics = c("w_perc","mean"), 
           base = example_of_base_information,
           conf = "ci") %>% print(n=1000)

```
