---
title: "Multicodes"
format: html
editor: visual
---

<br> 

## Set up

```{r packages, collapse=T, message=F, warning=F}
library(tidyverse)
library(srvyr)
library(flextable)
library(haven)
library(labelled)
library(huxtable)
```

<br> 

### Load data, set up functions

```{r}

## Load data
source("Set file paths.R")

## Load functions
source("Scripts/source_folder_r.R")
source_folder_r("Scripts", verbose = T)

data_table_presets <- function(data){
      DT::datatable(
    data,
    class = "compact stripe hover nowrp",
    options = list(
      scrollX = TRUE,
      pageLength = 25,
      autoWidth = TRUE
    ),
    rownames = FALSE
  ) 
}

```

<br>

### Base descriptions

Created for use when testing later. 

```{r}

var_descriptions <- rep("Self-completion questionnaire, asked of a random sub-set of respondents", 6)
names(var_descriptions) <- c("leftrigh", "welfare2", "libauth", "libauth2", "leftrigh2", "welfare3") 
var_descriptions

example_of_base_information <- base_information(
  data = df2,
  general_base = "Asked of all respondents", 
  specific_bases = var_descriptions
)

example_of_base_information[[1]]

example_of_base_information[[2]]

example_of_base_information[[3]]

example_of_base_information[[4]]

```

<br> 

## Identify Multicodes {.tabset}

### Steps overview

This code identifies variables with: a) a stem divider, I will use ": ", b) a matching set of values on the left hand side of the stem divider, c) No more than 2 unique values in its levels, and d) the same base size.

So, the variable labels will be split in two around ": ". A multicode set is one where all the left hand sides of the resulting variable are the same.

But how to identify matching sets?

Once done it will replace variable label with the left hand part of the stem.

The response levels will be filtered to 'yes' or equivalent. 'yes' will be a specifiable argument, e.g. could be 'mentioned'.

For simplicity, I'll **assume** binaries be coded consistently, e.g. people don't feed in a combination of yes/no and mentioned/not mentioned questions.

It will replace variable level == 'yes' with the right hand part of the stem.

Variable name will be reduced to the stem that is consistent across all variables in that set. Not dealt yet with the possibility that there is no consistent stem.

Base description will be updated to have a single base description for the variable as a whole, using the left hand part of the stem as the variable label.

This new base description will be silently added to the object with *base description* in it, in these trials that is `example_of_base_information`.

Should I then drop duplicates from the base description info? Probably, yes.

<br>

### Test data

#### Base information

```{r}

var_descriptions <- rep("Self-completion questionnaire", 5)
names(var_descriptions) <- c("Q1_OptionA", "Q1_OptionB", "Q1_OptionC", "Q1_OptionD", "Q1_OptionE") 


example_of_base_information2 <- base_information(
  data = survey_data,
  general_base = "Asked of all respondents", 
  specific_bases = var_descriptions
)

example_of_base_information2

example_of_base_information2[[1]]

example_of_base_information2[[2]]

example_of_base_information2[[3]]

example_of_base_information2[[4]]

```

<br>

#### Test table 1

```{r}

trial1 <- calc_stats(
    survey_data, 
    base = example_of_base_information2, 
    outcomes = c("Q1_OptionA", "Q1_OptionB", "Q1_OptionC", "Q1_OptionD", "Q1_OptionE", 
                 "Q2_ChoiceA", "Q2_ChoiceB", "Q2_ChoiceC", "Q2_ChoiceD", "Q2_ChoiceE",
                 "AgeGroup", "Satisfaction"),
    conf = "se") 

trial1 %>% print()
trial1 %>% glimpse

```

#### Test table 2

```{r}

trial2 <- calc_stats(
    survey_data, 
    base = example_of_base_information2, 
    outcomes = c("Q1_OptionA", "Q1_OptionB", "Q1_OptionC", "Q1_OptionD", "Q1_OptionE", 
                 "Q2_ChoiceA", "Q2_ChoiceB", "Q2_ChoiceC", "Q2_ChoiceD", "Q2_ChoiceE", 
                 "Satisfaction"),
    predictors = "AgeGroup",
    conf = "se") 

trial2 %>% print()
trial2 %>% glimpse
trial2$base_description %>% unique()
```

#### Test table 1

```{r}
trial3 <- calc_stats(
    survey_data, 
    base = example_of_base_information2, 
    outcomes = c("Q1_OptionA", "Q1_OptionB", "Q1_OptionC", "Q1_OptionD", "Q1_OptionE", 
                 "Q2_ChoiceA", "Q2_ChoiceB", "Q2_ChoiceC", "Q2_ChoiceD", "Q2_ChoiceE"),
    predictors = list(c("AgeGroup","Satisfaction")),
    conf = "se") 

trial3 %>% print()
trial3 %>% glimpse
trial3$base_description %>% unique()

```

<br><br>

### Convenience function to reduce variable names to a common stem

This takes a vector of variable names and returns a single character value with the common parts of the strings in that vector, assuming there is one.

```{r}

# Example vector of multi-coded variable names
vars <- c("Q1_OptionA", "Q1_OptionB", "Q1_OptionC", "Q1_OptionD", "Q1_OptionE")

# Find longest common prefix
common_prefix <- function(x) {
  split_names <- strsplit(x, "")
  min_length <- min(lengths(split_names))
  prefix <- character(0)
  for (i in seq_len(min_length)) {
    chars <- sapply(split_names, `[`, i)
    if (length(unique(chars)) == 1) {
      prefix <- c(prefix, chars[1])
    } else {
      break
    }
  }
  paste0(prefix, collapse = "")
}

write_function(common_prefix, folder = "Scripts")

common_prefix(vars)
# [1] "Q1_Option"

set1 <- c("Q2_Fruit_Apple", "Q2_Fruit_Banana", "Q2_Fruit_Cherry", "Q2_Fruit_Grape", "Q2_Fruit_Mango")
common_prefix(set1)

set6 <- c("Q4FruitApple", "Q4FruitBanana", "Q4FruitCherry", "Q4FruitGrape", "Q4FruitMango")
common_prefix(set6)

# If no common prefix, returns a string of zero length which will cause an error. Hmmmm. 
common_prefix(c("last","frui"))

```

<br>

### Intial variable screening

The first stage narrows the data frame received from `calc_stats` down to suitable rows:

1.  `stat` must equal "perc" or "count",\
2.  `o_lab` must contain ": ",\
3.  The outcome variable must contain either 1 or 2 levels,\
4.  Those levels must include the *relevant* value, for now "yes". Could be user specified.

<br>

5.  For these rows of data it them creates a variable called `left_stem`, which contains the values on the left hand side of ": ". This will be the variable label for the new multicode variable.

<br>

6.  There must be more than one variable with a consistent left_stem value.\
7.  The `base` value must be the same within unique values of left_stem.

The resulting output is a dataframe with only the relevant rows of data from the output of `calc_stats`.

```{r}

multis <- trial2 %>% 
  filter(stat == "perc" | stat == "count") %>% # Multicodes relevant only for categorical data
  filter(grepl(": ", o_lab)) %>% # Label must contain ": "
  group_by(across(contains(c("cross_break", "p_cat"))), outcome) %>% # Group by outcome variable
  mutate(lev_num = max(row_number())) %>% # Count number of levels in each variable
  group_by(outcome) %>% 
  mutate(lev_relevant = case_when(any(o_cat == "Yes") ~ 1, TRUE ~ 0)) %>% # Any of variable's levels equal yes? 
  filter(
    lev_num <= 2 & # Only use variables with 1 or 2 levels
    lev_relevant == 1 # Only use variables with a relevant level, here 'yes'
    )  %>% 
  mutate(
    left_stem = str_split_i(o_lab, ": ", 1) # Create left variable label stem 
    ) %>% 
  group_by(across(contains(c("crossbreak", "p_cat"))), left_stem) %>% # Group by predictors and left stem
  mutate(
    stem_count = n_distinct(outcome), # number of different variables with that variable stem 
    base_count = n_distinct(base) # Number of unique values in base
    ) %>% 
  filter(stem_count > 1) %>% # Only use variables where right stem recurs more than once
  filter(base_count == 1)  # Only use variables where base is unique within left_stem

multis

# Create an identifier vector for multicode rows from: 
#  -  cross_break (all the predictors), 
#  -  and the outcome variable.
# Then reduce that to a vector of unique values
multicode_row_identifiers <-  multis %>% unite(ident, c(cross_break, outcome)) %>% pull(ident) %>% unique
multicode_row_identifiers

# Use `multicode_row_identifiers` to drop these rows from the original table.
single_codes <- trial2 %>% unite(ident, c(cross_break, outcome), remove = F) %>% 
  filter(!ident %in% multicode_row_identifiers) %>% 
  select(-ident)

```

### Reorganise data identified as multicoded

```{r}

# The next step is done separately for each unique multicode set and predictor combination 
# Identified with left_stem2, created below. 
# Results returned as a list from map()

# If the column "cross_break" exists in the dataframe 'multis'...
if("cross_break" %in% names(multis)){
  # ...then create a new column 'left_stem2' by combining 'left_stem' and 'cross_break'
  multis <- multis %>% mutate(left_stem2 = paste0(left_stem, " - ", cross_break))
} else {
  # ...otherwise, just copy 'left_stem' into 'left_stem2'
  multis <- multis %>% mutate(left_stem2 = left_stem)
}

multis


# The following line is commented out — for testing 
# stem <- unique_stems[2]


# Get all unique values of 'left_stem2' in the data
unique_stems <- multis$left_stem2 %>% unique

# Loop over each unique value of 'left_stem2'
result <- map(unique_stems, function(stem) {
  
  # Filter 'multis' to only the rows matching the current stem
  multis2 <- multis %>% 
    filter(left_stem2 == stem) 
  
  # Save the original variable label from the first row (for later use)
  old_variable_label <- multis2$o_lab[1]
  
  # Step 1: Create a 'right_stem' by splitting 'o_lab' on ": " and taking the second part
  # Step 2: Replace 'o_lab' with the value of 'left_stem'
  multis2 <- multis2 %>%
    mutate(
      right_stem = str_split_i(o_lab, ": ", 2), 
      o_lab = left_stem
    ) %>% 
    # Step 3: Keep only rows where 'o_cat' == "Yes"
    filter(o_cat == "Yes") %>% 
    # Step 4: Replace 'o_cat' with 'right_stem' values, and shorten 'outcome' to its common prefix
    mutate(
      o_cat = right_stem, 
      outcome = common_prefix(outcome)
    ) 
  
  # Get the unique new variable name
  new_variable_name <- multis2$outcome %>% unique()
  # Get the unique new variable label
  new_variable_label <- multis2$o_lab %>% unique
  # Name the label vector with the new variable name
  names(new_variable_label) <- new_variable_name
  
  # Get the existing base description from the first row
  existing_base_description <- multis2$base_description[1]
  
  # If the base description contains " X ", split it into two parts
  if(str_detect(existing_base_description, " X ")){
    existing_base_description_2 <- str_split(existing_base_description, " X ") %>% unlist
  } else {
    # Otherwise, keep it as is
    existing_base_description_2 <- existing_base_description
  }
  
  # Create a logical index for which part(s) match the old variable label
  index <- str_detect(existing_base_description_2, old_variable_label)
  reverse_index <- !str_detect(existing_base_description_2, old_variable_label)
  
  # Extract the matching part(s) and remove anything after ":- "
  existing_base_description_3 <- existing_base_description_2[index] %>% str_split_i(., ":- ", 1)
  
  # Create a revised base label by appending the new variable label
  revised_base_label <- paste0(existing_base_description_3, ":- ", new_variable_label)
  names(revised_base_label) <- new_variable_name
  
  # If the base description originally had " X ", reassemble with the unchanged part(s)
  if(str_detect(existing_base_description, " X ")){
    remainder_of_base_description <- existing_base_description_2[reverse_index] 
    revised_base_description <- paste(
      revised_base_label, 
      remainder_of_base_description, 
      sep = " X ")
  } else {
    revised_base_description <- revised_base_label
  }
  
  # Update 'base_description' in the filtered dataset
  multis2 <- multis2 %>% mutate(base_description = revised_base_description)
  
  # Logical test: stop execution if the new variable name already exists in 'example_of_base_information2'
  if (new_variable_name %in% names(example_of_base_information2)) {
    stop("Error: New multicode variable name already in data.")
  } 
  
  # Return a list containing:
  # 1. The updated 'multis2' dataframe
  # 2. The revised base label
  # 3. The new variable label
  return(list(multis2, revised_base_label, new_variable_label))
  
}) 
# End of map() loop

# Combine all first elements of 'result' (the dataframes) into one big dataframe
tables <- bind_rows(map(result, ~(.x[[1]])))

# Extract all base labels from the results, flatten into one vector, and remove duplicates
new_base_descriptors <- map(result, ~(.x[[2]])) %>% unlist
new_base_descriptors <- new_base_descriptors[!duplicated(new_base_descriptors)]

# Extract all variable labels from the results, flatten, and remove duplicates
new_variable_labels <- map(result, ~(.x[[3]])) %>% unlist
new_variable_labels <- new_variable_labels[!duplicated(new_variable_labels)]

# Make a temporary copy of 'example_of_base_information2'
example_of_base_information2_temp <- example_of_base_information2

# Append new base descriptors and labels to positions [[2]], [[3]], and [[4]] of that object
example_of_base_information2_temp[[2]] <- c(example_of_base_information2[[2]], new_base_descriptors)
example_of_base_information2_temp[[3]] <- c(example_of_base_information2[[3]], new_variable_labels)
example_of_base_information2_temp[[4]] <- c(example_of_base_information2[[4]], new_variable_labels)

# Overwrite the original 'example_of_base_information2' object in the global environment with the updated version
example_of_base_information2 <<- example_of_base_information2_temp

multis2 <- tables %>% ungroup() %>% select(-lev_num, -lev_relevant, -left_stem, -stem_count, -base_count, -left_stem2, -right_stem)

# Review: original data, multicode data, and single code data...
trial2 %>% glimpse
multis2 %>% glimpse
multicode_row_identifiers %>% glimpse

# Bind single and multicode data together
bind_rows(single_codes, multis2)

```

<br>

### Fuction

```{r}

  # filter(stat == "perc" | stat == "count") %>% # Multicodes relevant only for categorical data
  # filter(grepl(": ", o_lab)) %>% # Label must contain ": "
  # group_by(across(contains(c("cross_break", "p_cat"))), outcome) %>% # Group by outcome variable
  # mutate(lev_num = max(row_number())) %>% # Count number of levels in each variable
  # group_by(outcome) %>% 
  # mutate(lev_relevant = case_when(any(o_cat == "Yes") ~ 1, TRUE ~ 0)) %>% # Any of variable's levels equal yes? 

# data <- trial3
# base_info <- example_of_base_information2
# rm(data)
# rm(base_info)
# rm(keep)

convert_multicodes <- function(
  data, 
  base_info = NULL, 
  keep = "Yes"){
  
  if(!is.null(base_info)){base_info_name_as_string <- deparse(substitute(base_info))}
  
  multis <- data %>% 
    filter(stat == "perc" | stat == "count" | stat == "w_count" | stat == "w_perc") %>% # Multicodes relevant only for categorical data
    filter(grepl(": ", o_lab)) %>% # Label must contain ": "
    
    # Count number of levels in each variable
    group_by(across(contains(c("cross_break", "p_cat"))), outcome) %>% # Group by outcome variable + crossbreak set + levels
    mutate(lev_num = max(row_number())) %>% 
    
    # Any of variable's levels equal yes?
    group_by(outcome) %>% 
    mutate(lev_relevant = case_when(any(o_cat == "Yes") ~ 1, TRUE ~ 0)) %>%  
    
    # filter non-relevant variables
    filter(
      lev_num <= 2 & # Only use variables with 1 or 2 levels
      lev_relevant == 1 # Only use variables with a relevant level, here 'yes'
      )  %>% 
    mutate(
      left_stem = str_split_i(o_lab, ": ", 1) # Create left variable label stem 
      ) %>% 
    group_by(across(contains(c("crossbreak", "p_cat"))), left_stem) %>% # Group by predictors and left stem
    mutate(
      stem_count = n_distinct(outcome), # number of different variables with that variable stem 
      base_count = n_distinct(base) # Number of unique values in base
      ) %>% 
    filter(stem_count > 1) %>% # Only use variables where right stem recurs more than once
    filter(base_count == 1)  # Only use variables where base is unique within left_stem
  
  if(nrow(multis) > 0){
  
  # Create an identifier vector for multicode rows from: 
  #  -  cross_break (all the predictors), 
  #  -  and the outcome variable.
  # Then reduce that to a vector of unique values
  multicode_row_identifiers <-  multis %>% unite(ident, contains(c("cross_break", "outcome"))) %>% pull(ident) %>% unique
  multicode_row_identifiers
  
  # Use `multicode_row_identifiers` to drop these rows from the original table.
  single_codes <- data %>% unite(ident, contains(c("cross_break", "outcome")), remove = F) %>% 
    filter(!ident %in% multicode_row_identifiers) %>% 
    select(-ident)

  # The next step is done separately for each unique multicode set and predictor combination 
  # Identified with left_stem2, created below. 
  # Results returned as a list from map()
  
  # If the column "cross_break" exists in the dataframe 'multis'...
  if("cross_break" %in% names(multis)){
    # ...then create a new column 'left_stem2' by combining 'left_stem' and 'cross_break'
    multis <- multis %>% mutate(left_stem2 = paste0(left_stem, " - ", cross_break))
  } else {
    # ...otherwise, just copy 'left_stem' into 'left_stem2'
    multis <- multis %>% mutate(left_stem2 = left_stem)
  }
  
  # Get all unique values of 'left_stem2' in the data
  unique_stems <- multis$left_stem2 %>% unique
  # stem <- unique_stems[[2]]
  
    # Loop over each unique value of 'left_stem2'
    result <- map(unique_stems, function(stem) {
    
    # Filter 'multis' to only the rows matching the current stem
    multis2 <- multis %>% filter(left_stem2 == stem) 
    
    # Save the original variable label from the first row (for later use)
    old_variable_label <- multis2$o_lab[1]
    
    # Step 1: Create a 'right_stem' by splitting 'o_lab' on ": " and taking the second part
    # Step 2: Replace 'o_lab' with the value of 'left_stem'
    multis2 <- multis2 %>% ungroup() %>%
      mutate(
        right_stem = str_split_i(o_lab, ": ", 2), 
        o_lab = left_stem
      ) %>% 
      # Step 3: Keep only rows where 'o_cat' == "Yes"
      filter(o_cat == "Yes") %>% 
      # Step 4: Replace 'o_cat' with 'right_stem' values, and shorten 'outcome' to its common prefix
      mutate(
        o_cat = right_stem, 
        outcome = common_prefix(outcome)
      ) 
    
    # Skip base description related steps where base_info NULL
    if(!is.null(base_info)){
        
      # Get the unique new variable name
      new_variable_name <- multis2$outcome %>% unique()
      # Get the unique new variable label
      new_variable_label <- multis2$o_lab %>% unique
      # Name the label vector with the new variable name
      names(new_variable_label) <- new_variable_name
      
      # Get the existing base description from the first row
      existing_base_description <- multis2$base_description[1]
      
      # If the base description contains " X ", split it into two parts
      if(str_detect(existing_base_description, " X ")){
        existing_base_description_2 <- str_split(existing_base_description, " X ") %>% unlist
      } else {
        # Otherwise, keep it as is
        existing_base_description_2 <- existing_base_description
      }
      
      # Create a logical index for which part(s) match the old variable label
      index <- str_detect(existing_base_description_2, old_variable_label)
      reverse_index <- !str_detect(existing_base_description_2, old_variable_label)
      
      # Extract the matching part(s) and remove anything after ":- "
      existing_base_description_3 <- existing_base_description_2[index] %>% str_split_i(., ":- ", 1)
      
      # Create a revised base label by appending the new variable label
      revised_base_label <- paste0(existing_base_description_3, ":- ", new_variable_label)
      names(revised_base_label) <- new_variable_name
      
      # If the base description originally had " X ", reassemble with the unchanged part(s)
      if(str_detect(existing_base_description, " X ")){
        remainder_of_base_description <- existing_base_description_2[reverse_index] 
        revised_base_description <- paste0(
          c(revised_base_label, remainder_of_base_description), 
          collapse = " X ")
      } else {
        revised_base_description <- revised_base_label
      }
      
      # Update 'base_description' in the filtered dataset
      multis2 <- multis2 %>% mutate(base_description = revised_base_description)
      
      # Logical test: drop existing variable names from 'base_info'
      if (new_variable_name %in% names(base_info[[3]])) {
        
        keep_item_2 <- which(!(base_info[[2]] %>% names()) %in% new_variable_name)
        keep_item_3 <- which(!(base_info[[3]] %>% names()) %in% new_variable_name)
        keep_item_4 <- which(!(base_info[[4]] %>% names()) %in% new_variable_name)
        base_info[[2]] <- base_info[[2]][keep_item_2]
        base_info[[3]] <- base_info[[3]][keep_item_3]
        base_info[[4]] <- base_info[[4]][keep_item_4]

        # stop("Error: New multicode variable name already in data.")
      } 
      
      # Where base description provided, return a list containing:
      #  1. The updated 'multis2' dataframe
      #  2. The revised base label
      #  3. The new variable label
      return(list(multis2, revised_base_label, new_variable_label))
    
    } else {
      
      return(list(multis2)) # Otherwise, simply return data frame, in a list so map() below will work
      
    }
    
    }) # End of map() loop
  
  # Combine all first elements of 'result' (the dataframes) into one big dataframe
  tables <- bind_rows(map(result, ~(.x[[1]])))
  
  # Skip base description related steps where base_info NULL
  if(!is.null(base_info)){
    
    # Extract all base labels from the results, flatten into one vector, and remove duplicates
    new_base_descriptors <- map(result, ~(.x[[2]])) %>% unlist
    new_base_descriptors <- new_base_descriptors[!duplicated(new_base_descriptors)]
    
    # Extract all variable labels from the results, flatten, and remove duplicates
    new_variable_labels <- map(result, ~(.x[[3]])) %>% unlist
    new_variable_labels <- new_variable_labels[!duplicated(new_variable_labels)]
    
    # Make a temporary copy of 'base_info'
    example_of_base_info2_temp <- base_info
    
    # If those variable names already exist in base descriptions information, then drop them...
    base_info[[2]] <- base_info[[2]][which(!base_info[[2]] %in% new_base_descriptors)]
    base_info[[3]] <- base_info[[3]][which(!base_info[[3]] %in% new_variable_labels)]
    base_info[[4]] <- base_info[[4]][which(!base_info[[4]] %in% new_variable_labels)]

    # Append new base descriptors and labels to positions [[2]], [[3]], and [[4]] of that object
    example_of_base_info2_temp[[2]] <- c(base_info[[2]], new_base_descriptors)
    example_of_base_info2_temp[[3]] <- c(base_info[[3]], new_variable_labels)
    example_of_base_info2_temp[[4]] <- c(base_info[[4]], new_variable_labels)
    
    # Overwrite the original 'base_info' object in the global environment with the updated version
    assign(base_info_name_as_string, example_of_base_info2_temp, envir = .GlobalEnv)
    # base_info <<- example_of_base_info2_temp
  
  }
  
  # Create multicode object to export
  multis2 <- tables %>% 
    ungroup() %>% # Otherwise, cannot drop left_stem
    # Drop temporary variables
    select(-lev_num, -lev_relevant, -left_stem, -stem_count, -base_count, -left_stem2, -right_stem)
  
  # Bind single and multicode data together
  multicoded_and_single_code_data <- bind_rows(single_codes, multis2)
  
  return(multicoded_and_single_code_data)
  
  } else {return(data)}
  
}

write_function(convert_multicodes, folder = "Scripts")


```

<br>

#### Test multicode conversion {.tabset}

##### Test 1

```{r}

convert_multicodes(
  data = trial1, 
  base_info = example_of_base_information2, 
  keep = "Yes") %>% df_to_dense_flextable()

```

<br>

##### Test 2

```{r}
convert_multicodes(
  data = trial2, 
  base_info = example_of_base_information2, 
  keep) %>% 
  df_to_dense_flextable()

```

<br>

##### Test 3

```{r}
rm(base_info)
convert_multicodes(
  data = trial3 %>% mutate(base=NA,base_description=NA), 
  base_info = NULL,
  # base_info = example_of_base_information2, 
  keep) %>% 
  df_to_dense_flextable()

convert_multicodes(
  data = trial3, 
  base_info = example_of_base_information2,
  keep) %>% 
  df_to_dense_flextable()

```

<br><br><br>

