---
title: "Weighted statistics"
format: html
editor: visual
---

<br> 

## Set up

```{r packages, collapse=T, message=F, warning=F}
library(tidyverse)
library(srvyr)
library(flextable)
library(haven)
library(labelled)
library(huxtable)
```

<br> 

### Load data, set up functions

```{r}

## Load data
source("Set file paths.R")

## Load functions
source("Scripts/source_folder_r.R")
source_folder_r("Scripts", verbose = T)

data_table_presets <- function(data){
      DT::datatable(
    data,
    class = "compact stripe hover nowrp",
    options = list(
      scrollX = TRUE,
      pageLength = 25,
      autoWidth = TRUE
    ),
    rownames = FALSE
  ) 
}

```

<br>

### Base descriptions

Created for use when testing later. 

```{r}

var_descriptions <- rep("Self-completion questionnaire, asked of a random sub-set of respondents", 6)
names(var_descriptions) <- c("leftrigh", "welfare2", "libauth", "libauth2", "leftrigh2", "welfare3") 
var_descriptions

example_of_base_information <- base_information(
  data = df2,
  general_base = "Asked of all respondents", 
  specific_bases = var_descriptions
)

```

## Weighted functions 

* Numeric variables - `weighted_mean`.    
* Numeric variables - `weighted_median`.    
* Numeric variables - `weighted_sum`.    
* Categorical variables - `weighted_perc`.    
* Categorical variables - `weighted_count`.      


### Weighted means

```{r weighted mean}

weighted_mean <- function(
    data, # a srvyr design object
    outcomes, # a character vector of outcome variables
    predictors = NULL, # a list, each element containing a character vector of predictor variables
    conf = NULL, # "se" or "ci"; returns either standard error or confidence intervals
    base = NULL
) {suppressMessages({suppressWarnings({
  
  output <- map(outcomes, function(cur_outcome) {
    
    base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = cur_outcome)) # edit
    
    # Remove missing data
    one_total_table <- data %>% 
      filter(!is.na(.data[[cur_outcome]])) %>% 
      summarise(estimate = survey_mean(!!sym(cur_outcome), vartype = conf), 
                base = unweighted(n())) %>% 
        mutate("{cur_outcome}" := "w_mean") %>% 
        mutate(outcome = cur_outcome) %>% 
        rename(any_of(c(o_cat = cur_outcome))) %>% 
        mutate(o_lab = attributes(data$variables[[cur_outcome]])$label) %>% 
      # edit
      mutate(base_description = base_defintion) # descriptor label for base 

    # Create cross-breaks
    if(!is.null(predictors)){
    predictor_tables <- map(predictors, function(cur_predictor) { 
      
            # Handle cases with and without predictor variables
        if (length(cur_predictor) > 0) {
          
          # Vector containing predictors and outcomes
          predictor_and_outcome <- c(cur_predictor, cur_outcome)
          base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = predictor_and_outcome)) # edit
          
          one_predictor_table <- data %>%
            # Filter missing values
            filter(rowSums(across(all_of(predictor_and_outcome), ~ is.na(.))) == 0) %>%
            # Group data
            group_by(across(all_of(cur_predictor))) %>% 
            # Weighted mean + base sizes, with grouping vars
            summarise(estimate = survey_mean(!!sym(cur_outcome), vartype = conf), 
                      base = unweighted(n())) %>% 
            # Added for consistency when merged with categorical outcome tables. 
            mutate("{cur_outcome}" := "w_mean") %>% 
            # Standardise names so can stack results across different predictors and outcomes. 
            standardise_names(data = data, preds = cur_predictor, out_var = cur_outcome) %>%
            mutate(cross_break = paste0(cur_predictor, collapse = "_X_")) %>%
            # edit
            mutate(base_description = base_defintion) # descriptor label for base 
        
        }
      
      return(one_predictor_table)
      
    })
    
    predictor_tables <- bind_rows(predictor_tables)
    
    } # Predictors ends
    
    # Bind crossbreaks and frequency table together
    if(!is.null(predictors)){table_for_one_outcome <- bind_rows(one_total_table, predictor_tables)
    } else {table_for_one_outcome <- one_total_table}
    
    table_for_one_outcome <- table_for_one_outcome %>%
      # Record statistic calculated
      mutate(stat = "w_mean") %>%
      # Add 'Total' to predictor category variables for frequency section of the table.
      mutate(across(contains(c("cross_break", "predictor", "p_lab", "p_cat")), ~case_when(is.na(.x) ~ "Total", TRUE ~ .x))) %>%
      # Reorder variables
      select(contains(c("cross_break", "predictor", "p_lab", "p_cat")), outcome, o_lab, o_cat, stat, contains("estimate"), base, base_description) # edit
    
    if(!is.null(conf)){
    if(conf == "ci"){
      table_for_one_outcome <- table_for_one_outcome %>% 
        mutate(estimate_ci = paste0(as.character(estimate_low), " - ", as.character(estimate_upp)))}
    } else { 
      table_for_one_outcome <- table_for_one_outcome %>% mutate(estimate_se = "-", .after = estimate)
      }

    return(table_for_one_outcome)
    
  }) # Outcomes loop ends 
  
  output <- output %>% bind_rows() %>% mutate(unweighted_n = base)
  
  return(output)
  
})})
}

write_function(weighted_mean, folder = "Scripts")

```

### Trials 

#### Trial 1

```{r}

trial1 <- weighted_mean(df_svy, outcomes = c("libauth","leftrigh"), predictors = list("RSex"))
trial1 %>% glimpse
trial1 %>% print()
print(trial1)
```

<br> 

#### Trial 2

```{r}

trial2 <- weighted_mean(df_svy, outcomes = c("libauth","leftrigh"), predictors = list("RSex","RAgeCat"), conf = "se") 
trial2 %>% glimpse
trial2 %>% print()

```

<br> 

#### Trial 3

```{r}

trial3 <- weighted_mean(df_svy, outcomes = c("libauth","leftrigh"), predictors = list(c("RSex","RAgeCat")), base = example_of_base_information) 
trial3 %>% glimpse
trial3 %>% print()
trial3$base_description %>% unique

```

<br> 

#### Trial 4

```{r}

trial4 <- weighted_mean(df_svy, outcomes = c("libauth"), predictors = list(c("RSex","RAgeCat")), conf = "ci") 
trial4 %>% glimpse
trial4 %>% print()

```

<br> 

#### Trial 5

```{r}

trial5 <- weighted_mean(df_svy, outcomes = c("libauth","welfare2","leftrigh"), conf = "ci", base = example_of_base_information) 
trial5 %>% glimpse
trial5 %>% print()


```

<br> 

## Weighted medians

```{r weighted median}

weighted_median <- function(
    data, # a srvyr design object
    outcomes, # a character vector of outcome variables
    predictors = NULL, # a list, each element containing a character vector of predictor variables
    conf = NULL, # "se" or "ci"; returns either standard error or confidence intervals 
    base = NULL
) {suppressMessages({suppressWarnings({
  
  output <- map(outcomes, function(cur_outcome) {
    # Remove missing data
    base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = cur_outcome)) # edit

    one_total_table <- data %>% 
      filter(!is.na(.data[[cur_outcome]])) %>% 
      summarise(estimate = survey_median(!!sym(zap_labels(cur_outcome)), vartype = conf), 
                base = unweighted(n())) %>% 
        mutate("{cur_outcome}" := "w_median") %>% 
        mutate(outcome = cur_outcome) %>% 
        rename(any_of(c(o_cat = cur_outcome))) %>% 
        mutate(o_lab = attributes(data$variables[[cur_outcome]])$label) %>% 
      mutate(base_description = base_defintion) # descriptor label for base 
  
    # Create cross-breaks
    if(!is.null(predictors)){
    predictor_tables <- map(predictors, function(cur_predictor) { 
      
            # Handle cases with and without predictor variables
        if (length(cur_predictor) > 0) {
          
          # Vector containing predictors and outcomes
          predictor_and_outcome <- c(cur_predictor, cur_outcome)
          base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = predictor_and_outcome))
          
          one_predictor_table <- data %>%
            # Filter missing values
            filter(rowSums(across(all_of(predictor_and_outcome), ~ is.na(.))) == 0) %>%
            # Group data
            group_by(across(all_of(cur_predictor))) %>% 
            # Weighted median + base sizes, with grouping vars
            summarise(estimate = survey_median(!!sym(zap_labels(cur_outcome)), vartype = conf),
                      base = unweighted(n())) %>% 
            # Added for consistency when merged with categorical outcome tables. 
            mutate("{cur_outcome}" := "w_median") %>% 
            # Standardise names so can stack results across different predictors and outcomes. 
            standardise_names(data = data, preds = cur_predictor, out_var = cur_outcome) %>%
            mutate(cross_break = paste0(cur_predictor, collapse = "_X_")) %>%
            mutate(base_description = base_defintion) # descriptor label for base 
        }
      
      return(one_predictor_table)
      
    })
    
    predictor_tables <- bind_rows(predictor_tables)
    
    } # Predictors ends
    
    # Bind crossbreaks and frequency table together
    if(!is.null(predictors)){table_for_one_outcome <- bind_rows(one_total_table, predictor_tables)
    } else {table_for_one_outcome <- one_total_table}
    
    table_for_one_outcome <- table_for_one_outcome %>%
      # Record statistic calculated
      mutate(stat = "w_median") %>%
      # Add 'Total' to predictor category variables for frequency section of the table.
      mutate(across(contains(c("cross_break", "predictor", "p_lab", "p_cat")), ~case_when(is.na(.x) ~ "Total", TRUE ~ .x))) %>%
      # Reorder variables
      select(contains(c("cross_break", "predictor", "p_lab", "p_cat")), outcome, o_lab, o_cat, stat, contains("estimate"), base, base_description) 
    
    if(!is.null(conf)){
      if(conf == "ci"){
        table_for_one_outcome <- table_for_one_outcome %>% 
          mutate(estimate_ci = paste0(as.character(estimate_low), " - ", as.character(estimate_upp)))}
    } else { 
      table_for_one_outcome <- table_for_one_outcome %>% mutate(estimate_se = "-", .after = estimate)
    }

    return(table_for_one_outcome)
    
  }) # Outcomes loop ends 
  
  output <- output %>% bind_rows() %>% mutate(unweighted_n = base)
  
  return(output)
  
})})
}

write_function(weighted_median, folder = "Scripts")

```

<br> 

### Trials 

#### Trial 1

```{r}

trial1 <- weighted_median(df_svy, outcomes = c("libauth","leftrigh"), predictors = list("RSex","RAgeCat")) 
trial1 %>% glimpse()
trial1 %>% print()

```

<br> 

#### Trial 2

```{r}

trial2 <- weighted_median(df_svy, outcomes = c("libauth"), predictors = list(c("RSex","RAgeCat","skipmeal"))) 
trial2 %>% glimpse()
trial2 %>% print()

```

<br> 

#### Trial 3

```{r}

trial3 <- weighted_median(df_svy, outcomes = c("libauth"), conf = "ci", base = example_of_base_information) 
trial3 %>% glimpse()
trial3 %>% print()

```

<br> 

## Weighted sums

```{r weighted sum}

weighted_sum <- function(
    data, # a srvyr design object
    outcomes, # a character vector of outcome variables
    predictors = NULL, # a list, each element containing a character vector of predictor variables
    conf = NULL, # "se" or "ci"; returns either standard error or confidence intervals 
    base = NULL
) {suppressMessages({suppressWarnings({
  
  output <- map(outcomes, function(cur_outcome) {
    
    base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = cur_outcome)) 
    
    # Remove missing data
    one_total_table <- data %>% 
      filter(!is.na(.data[[cur_outcome]])) %>% 
      summarise(estimate = survey_total(!!sym(zap_labels(cur_outcome)), vartype = conf), 
                base = unweighted(n())) %>% 
        mutate("{cur_outcome}" := "w_sum") %>%
        mutate(outcome = cur_outcome) %>% 
        rename(any_of(c(o_cat = cur_outcome))) %>% 
        mutate(o_lab = attributes(data$variables[[cur_outcome]])$label) %>% 
      mutate(base_description = base_defintion) # descriptor label for base 
  
    # Create cross-breaks
    if(!is.null(predictors)){
    predictor_tables <- map(predictors, function(cur_predictor) { 
      
            # Handle cases with and without predictor variables
        if (length(cur_predictor) > 0) {
          
          # Vector containing predictors and outcomes
          predictor_and_outcome <- c(cur_predictor, cur_outcome)
          base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = predictor_and_outcome)) 
          
          one_predictor_table <- data %>%
            # Filter missing values
            filter(rowSums(across(all_of(predictor_and_outcome), ~ is.na(.))) == 0) %>%
            # Group data
            group_by(across(all_of(cur_predictor))) %>% 
            # Weighted median + base sizes, with grouping vars
            summarise(estimate = survey_total(!!sym(zap_labels(cur_outcome)), vartype = conf),
                      base = unweighted(n())) %>% 
            # Added for consistency when merged with categorical outcome tables. 
            mutate("{cur_outcome}" := "w_sum") %>%
            # Standardise names so can stack results across different predictors and outcomes. 
            standardise_names(data = data, preds = cur_predictor, out_var = cur_outcome) %>%
            mutate(cross_break = paste0(cur_predictor, collapse = "_X_")) %>%
            mutate(base_description = base_defintion) # descriptor label for base 
        }
      
      return(one_predictor_table)
      
    })
    
    predictor_tables <- bind_rows(predictor_tables)
    
    } # Predictors ends
    
    # Bind crossbreaks and frequency table together
    if(!is.null(predictors)){table_for_one_outcome <- bind_rows(one_total_table, predictor_tables)
    } else {table_for_one_outcome <- one_total_table}
    
    table_for_one_outcome <- table_for_one_outcome %>%
      mutate(stat = "w_sum") %>%
      # Add 'Total' to predictor category variables for frequency section of the table.
      mutate(across(contains(c("cross_break", "predictor", "p_lab", "p_cat")), ~case_when(is.na(.x) ~ "Total", TRUE ~ .x))) %>%
      # Reorder variables
      select(contains(c("cross_break", "predictor", "p_lab", "p_cat")), outcome, o_lab, o_cat, stat, contains("estimate"), base, base_description) 
        
    if(!is.null(conf)){
      if(conf == "ci"){
        table_for_one_outcome <- table_for_one_outcome %>% 
          mutate(estimate_ci = paste0(as.character(estimate_low), " - ", as.character(estimate_upp)))}
    } else { 
      table_for_one_outcome <- table_for_one_outcome %>% mutate(estimate_se = "-", .after = estimate)
    }

    return(table_for_one_outcome)
    
  }) # Outcomes loop ends 
  
  output <- output %>% bind_rows() %>% mutate(unweighted_n = base)
  
  return(output)
  
})})
}

write_function(weighted_sum, folder = "Scripts")


```

<br>

### Trials 

#### Trial 1

```{r}
trial1 <- weighted_sum(df_svy, outcomes = c("libauth","leftrigh"), predictors = list("RSex","RAgeCat")) 
trial1 %>% glimpse()
trial1 %>% print()
```

<br> 

#### Trial 2

```{r}
trial2 <- weighted_sum(df_svy, outcomes = c("libauth"), predictors = list(c("RSex","RAgeCat","skipmeal")), base = example_of_base_information)
trial2 %>% glimpse
trial2 %>% print()
```

<br> 

#### Trial 3

```{r}

trial3 <- weighted_sum(df_svy, outcomes = c("libauth", "leftrigh"), predictors = list("RSex"), conf = "ci")
trial3 %>% glimpse()
trial3 %>% print()

```

<br><br> 

## Weighted percentages

```{r weighted percentages}

weighted_perc <- function(
    data, # a srvyr design object
    outcomes, # a character vector of outcome variables
    predictors = NULL, # a list, each element containing a character vector of predictor variables
    conf = NULL, # "se" or "ci"; returns either standard error or confidence intervals 
    base = NULL
) {suppressMessages({suppressWarnings({
  
  output <- map(outcomes, function(cur_outcome) {
    
    base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = cur_outcome)) # edit
    
    # Remove missing data
    one_total_table <- data %>% 
      filter(!is.na(.data[[cur_outcome]])) %>% 
      group_by(across(all_of(cur_outcome))) %>% 
      summarise(estimate = survey_prop(vartype = conf), 
                unweighted_n = unweighted(n())) %>% 
      mutate(base = sum(unweighted_n, na.rm = T)) %>%
      mutate(outcome = cur_outcome) %>% 
      rename(any_of(c(o_cat = cur_outcome))) %>% 
      mutate(o_lab = attributes(data$variables[[cur_outcome]])$label) %>% 
      mutate(base_description = base_defintion) # descriptor label for base 
  
    # Create cross-breaks
    if(!is.null(predictors)){
    predictor_tables <- map(predictors, function(cur_predictor) { 
  
            # Handle cases with and without predictor variables
        if (length(cur_predictor) > 0) {
          
          # Vector containing predictors and outcomes
          predictor_and_outcome <- c(cur_predictor, cur_outcome)
          base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = predictor_and_outcome)) # edit
          
          one_predictor_table <- data %>%
            # Filter missing values
            filter(rowSums(across(all_of(predictor_and_outcome), ~ is.na(.))) == 0) %>%
            # Group data
            group_by(across(all_of(predictor_and_outcome))) %>% 
            # Weighted percentage + base sizes, with grouping vars
            summarise(estimate = survey_prop(vartype = conf), 
                      unweighted_n = unweighted(n())) %>% 
            mutate(base = sum(unweighted_n, na.rm = T)) %>%
            # Standardise names so can stack results across different predictors and outcomes. 
            standardise_names(data = data, preds = cur_predictor, out_var = cur_outcome) %>%
            mutate(cross_break = paste0(cur_predictor, collapse = "_X_")) %>%
            mutate(base_description = base_defintion) # descriptor label for base 
        }
      
      return(one_predictor_table)
      
    })
    
    predictor_tables <- bind_rows(predictor_tables)
    
    } # Predictors ends
    
    # Bind crossbreaks and frequency table together
    if(!is.null(predictors)){table_for_one_outcome <- bind_rows(one_total_table, predictor_tables)
    } else {table_for_one_outcome <- one_total_table}
    
    table_for_one_outcome <- table_for_one_outcome %>%
      mutate(stat = "w_perc") %>%
      # Add 'Total' to predictor category variables for frequency section of the table.
      mutate(across(contains(c("cross_break", "predictor", "p_lab", "p_cat")), ~case_when(is.na(.x) ~ "Total", TRUE ~ .x))) %>%
      # Reorder variables
      select(contains(c("cross_break", "predictor", "p_lab", "p_cat")), outcome, o_lab, o_cat, stat, contains("estimate"), base, base_description, unweighted_n) 
    
    if(!is.null(conf)){
      if(conf == "ci"){
        table_for_one_outcome <- table_for_one_outcome %>% 
          mutate(estimate_ci = paste0(as.character(estimate_low), " - ", as.character(estimate_upp)))}
    } else { 
      table_for_one_outcome <- table_for_one_outcome %>% mutate(estimate_se = "-", .after = estimate)
    }

    return(table_for_one_outcome)
    
  }) # Outcomes loop ends 
  
  output <- output %>% bind_rows() %>% mutate(unweighted_n = base)
  
  return(output)
  
})})
}

write_function(weighted_perc, folder = "Scripts")


```

<br> 

### Trials 

<br> 

#### Trial 1

```{r}
trial <- weighted_perc(df_svy, outcomes = c("skipmeal"), predictors = list("RSex","RAgeCat")) 
trial %>% glimpse()
trial %>% print()

```

<br> 

#### Trial 2

```{r}
trial2 <- weighted_perc(df_svy, outcomes = c("MuchPov"), predictors = list(c("RSex","RAgeCat","skipmeal")), base = example_of_base_information) 
trial2 %>% glimpse
trial2 %>% print()
```

<br><br> 

## Weighted count

```{r weighted count}

weighted_count <- function(
    data, # a srvyr design object
    outcomes, # a character vector of outcome variables
    predictors = NULL, # a list, each element containing a character vector of predictor variables
    conf = NULL, # "se" or "ci"; returns either standard error or confidence intervals 
    base = NULL
) {suppressMessages({suppressWarnings({
  
  output <- map(outcomes, function(cur_outcome) {
    
    base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = cur_outcome)) # edit

    # Remove missing data
    one_total_table <- data %>% 
      filter(!is.na(.data[[cur_outcome]])) %>% 
      group_by(across(all_of(cur_outcome))) %>% 
      summarise(estimate = survey_total(vartype = conf), 
                unweighted_n = unweighted(n())) %>% 
      mutate(base = sum(unweighted_n, na.rm = T)) %>%
      mutate(outcome = cur_outcome) %>% 
      rename(any_of(c(o_cat = cur_outcome))) %>% 
      mutate(o_lab = attributes(data$variables[[cur_outcome]])$label) %>% 
      mutate(base_description = base_defintion) # descriptor label for base 
  
  
    # Create cross-breaks
    if(!is.null(predictors)){
    predictor_tables <- map(predictors, function(cur_predictor) { 
  
            # Handle cases with and without predictor variables
        if (length(cur_predictor) > 0) {
          
          # Vector containing predictors and outcomes
          predictor_and_outcome <- c(cur_predictor, cur_outcome)
          base_defintion <- ifelse(is.null(base), NA, create_bases(base_info = base, variables = predictor_and_outcome)) # edit
          
          one_predictor_table <- data %>%
            # Filter missing values
            filter(rowSums(across(all_of(predictor_and_outcome), ~ is.na(.))) == 0) %>%
            # Group data
            group_by(across(all_of(predictor_and_outcome))) %>% 
            # Weighted percentage + base sizes, with grouping vars
            summarise(estimate = survey_total(vartype = conf), 
                unweighted_n = unweighted(n())) %>% 
            mutate(base = sum(unweighted_n, na.rm = T)) %>%
            # Standardise names so can stack results across different predictors and outcomes. 
            standardise_names(data = data, preds = cur_predictor, out_var = cur_outcome) %>%
            mutate(cross_break = paste0(cur_predictor, collapse = "_X_")) %>%
            mutate(base_description = base_defintion) # descriptor label for base 
        }
      
      return(one_predictor_table)
      
    })
    
    predictor_tables <- bind_rows(predictor_tables)
    
    } # Predictors ends
    
    # Bind crossbreaks and frequency table together
    if(!is.null(predictors)){table_for_one_outcome <- bind_rows(one_total_table, predictor_tables)
    } else {table_for_one_outcome <- one_total_table}
    
    table_for_one_outcome <- table_for_one_outcome %>%
      mutate(stat = "w_count") %>%
      # Add 'Total' to predictor category variables for frequency section of the table.
      mutate(across(contains(c("cross_break", "predictor", "p_lab", "p_cat")), ~case_when(is.na(.x) ~ "Total", TRUE ~ .x))) %>%
      # Reorder variables
      select(contains(c("cross_break", "predictor", "p_lab", "p_cat")), outcome, o_lab, o_cat, stat, contains("estimate"), base, base_description, unweighted_n) 

    if(!is.null(conf)){
      if(conf == "ci"){
        table_for_one_outcome <- table_for_one_outcome %>% 
          mutate(estimate_ci = paste0(as.character(estimate_low), " - ", as.character(estimate_upp)))}
    } else { 
      table_for_one_outcome <- table_for_one_outcome %>% mutate(estimate_se = "-", .after = estimate)
    }
    
    return(table_for_one_outcome)
    
  }) # Outcomes loop ends 
  
  output <- output %>% bind_rows()
  
  return(output)
  
})})
}

write_function(weighted_count, folder = "Scripts")


```

<br>

### Trials 

#### Trial 1

```{r}

trial <- weighted_count(df_svy, outcomes = c("skipmeal"), predictors = list("RSex","RAgeCat")) 
trial %>% glimpse()
trial %>% print()

```

<br> 

#### Trial 2

```{r}

trial <- weighted_count(df_svy, outcomes = c("MuchPov"), predictors = list(c("RSex","RAgeCat","skipmeal")), base = example_of_base_information) 
trial %>% glimpse
trial %>% print()

```

<br>

#### Trial 3

```{r}

trial <- weighted_count(df_svy, outcomes = c("MuchPov"), conf = "ci") 
trial %>% glimpse()
trial %>% print()

```

<br>
